---
title: "re_analysis_dsouza_2020"
author: "Rodrigo Dal Ben"
date: "July, 6, 2020"
output: html_document
---

Article: Iliaei, S. P., Killam, H., Dal Ben, R., & Byers-Heinlein, K. (under review). The bilingual advantage in infancy: Evidence from 7- and 20-month-olds.

This script was adapted from the analysis script for Study 1a and Study 2. 
Original author: Hilary Kilam
Date: January 27, 2020.

Re-analyse D'Souza data with the, fine-grained, mixed-effects models used in the Study 1a and Study 2. 
Doubts and suggestions: dalbenwork@gmail.com

D'Souza et al. (2020) references: 
- article: 10.1098/rsos.180191) 
- OSF: https://osf.io/53gh2/
- Dryad: 10.5061/dryad.3n5tb2rc6 

Doubts and suggestions: dalbenwork@gmail.com

# Load library

```{r}
knitr::opts_chunk$set(echo = FALSE)

## Load packages
library(here)
library(tidyverse)
library(janitor)
library(readxl)
library(patchwork)
library(grDevices)
library(RColorBrewer)

library(lme4)
library(effects)
library(emmeans)
library(ggeffects)
library(interactions)
library(car)
library(ez)

library(apa)
library(apaTables)
library(gt)
library(flextable)
library(sjPlot)

library(eyetrackingR) 

options(scipen = 999) # remove scientific notation

kovacs09 <- "Kovács & Mehler 2009"

## Define minimum looking and minimum trial numbers for this study
MIN_LOOK_PROPORTION <- .5
MIN_NUMBER_TRIALS <- 5
```

# Load data

Analysis were ran for the filtered sample (n = 51), as reported on the main article, and on the full sample (n = 102), as reported on the supplementary materials.

```{r}
load(here("03_output/01_wrangling/data_full_trials.rda")) # data_full_trials = filtered 51 sample - main article
load(here("03_output/01_wrangling/dataset_exp1_v3.rda")) # dataset_exp1_v3 = full 102 sample - comparison on supplements
```

# Descriptives 

* Only one age group (7 ~ 9 months);
* No vocabulary measures;
* All exclusions have been made on "reanalysis_dsouza_wrangling.R" script;
* "Maternal education" is replaced by SES (Social Economic Status): "a composite of four weighted scores based on the carers’ (1) postcode (as an index of socioeconomic deprivation), (2) education attainment, (3) household income and (4) occupation." (D'Souza et al., 2020, p. 4)

```{r}
###------------------------------------------------FINAL SAMPLE COUNTS PER AGE--------------------------------------
#dataset_exp1_v3 %>% 
data_full_trials %>% 
  distinct(id, gender, age_in_days) %>% 
  summarize(count = length(id),
            avg_age_days = floor(mean(age_in_days)),
            min_age_days = min(age_in_days),
            max_age_days = max(age_in_days),
            num_female = sum(gender == 1))
  
###-----------------------------------------------FINAL SAMPLE COUNTS PER LANG BACKGROUND------------------------------
#dataset_exp1_v3 %>%
data_full_trials %>% 
  distinct(id, language) %>% 
  group_by(language) %>%
  summarize(count = length(id))

###----------------------------------------------------------COMPARE GROUPS------------------------------
age_summary <- 
  #dataset_exp1_v3 %>%
  data_full_trials %>% 
  distinct(id, age_in_days, language)

summary(age_summary$age_in_days)

ggplot(age_summary, aes(age_in_days)) + 
  geom_histogram(binwidth = 5) + # adjusted
  facet_wrap(~ language)

t.test(age_in_days ~ language, data = age_summary) # no age diff between mono and bi

# gender
gender_summary <- 
  #dataset_exp1_v3 %>%
  data_full_trials %>% 
  distinct(id, gender, language) %>% 
  group_by(language) %>% 
  count(gender)

t.test(n ~ language, data = gender_summary) # no gender diff between mono and bi

###----------------------------------------------------------COMPARE MATERNAL EDUCATION------------------------------
# obs. using ses_score (Social Economic Status)
ses_summary <- 
  #dataset_exp1_v3 %>%
  data_full_trials %>% 
  distinct(id, age_in_days, language, ses_score)

ggplot(ses_summary, aes(ses_score)) + 
  geom_histogram(binwidth = 0.05) + # adjusted
  facet_wrap(~ language)

t.test(ses_score ~ language, data = ses_summary) # no ses diff between mono and bi
```

# Language tables

D'Souza et al. (2020) article and supplementals do not provide information about participants' dominant/other languages or the percentages of exposure to different languages.
Unable to produce language tables.

# EyeTrackingR Data

```{r}
###----------------------------------------------------CREATE EYETRACKINGR DATA FOR FULL TRIAL PLOTS
data_eyetracking_full_trials <- make_eyetrackingr_data(data_full_trials, #dataset_exp1_v3, 
                                participant_column = "id",
                                trial_column = "trial_name", 
                                time_column = "trial_from_zero",
                                trackloss_column = "trackloss", 
                                aoi_columns = c('target', 'circle', 'distractor'), 
                                treat_non_aoi_looks_as_missing = TRUE)

full_trial_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 0,
                                     window_end_time = 6600, rezero = TRUE, remove = TRUE)

data_time_series_full <- make_time_sequence_data(full_trial_window,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "trial_type", "trial_num", "ses_score", "exposure"), 
                                         aois = c("circle", "target", "distractor"))

###---------------------------------------------CREATE EYETRACKINGR DATA FOR ANTICIPATION PERIOD PLOTS
data_eyetracking_antic_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 3200, # event = antecipOnset + 150
                                     window_end_time = 4200, # event = rewardOnset + 150
                                     rezero = TRUE, remove = TRUE)

trackloss <- trackloss_analysis(data = data_eyetracking_antic_window)

data_eyetracking_clean <- clean_by_trackloss(data = data_eyetracking_antic_window, trial_prop_thresh = .5) #this eliminates all data from trials with 50% or more trackloss (we merged the baby IDs who made it through to the final sample back with the full data, so makes sense we will re-exclude some trials here)

data_eyetracking_clean_nocircle <- make_eyetrackingr_data(data_full_trials, #dataset_exp1_v3, 
                                participant_column = "id",
                                trial_column = "trial_name", 
                                time_column = "trial_from_zero",
                                trackloss_column = "trackloss", 
                                aoi_columns = c('target', 'distractor'), # this will calculate prop looking in relation to just target vs distractor
                                treat_non_aoi_looks_as_missing = TRUE) %>%
  subset_by_window(window_start_time = 3200,
                   window_end_time = 4200, rezero = TRUE, remove = TRUE) %>%
  clean_by_trackloss(trial_prop_thresh = .5)

data_time_series_antic <- make_time_sequence_data(data_eyetracking_clean,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "trial_type", "trial_num", "ses_score", "exposure"),
                                         aois = c("circle", "target", "distractor"))
```


# Time Series Plots

```{r time_series_plots, echo = FALSE}
###----------------------------------------------------------PLOT FULL TRIALS-----------------------------------------
line_colors <- c("#D55E00", "#0072B2") # color-blind friendly
line_types <- c("dotted", "solid", "dashed")
line_sizes <- c(.6, 0.5, 0.5)
facet_text <- data.frame(trial_labels = c("Trial 1"), 
                         language = c("Monolinguals"), 
                         aoi = c("target"), 
                         Time = c(3650), 
                         trial_type_labs = c("Training", "Test"), 
                         prop_looking = c(.875), 
                         label = c("Anticipation period"))

time_series_full_trial <-
  data_time_series_full %>%
  filter(Time >= 2400 & Time <= 5000) %>% 
  mutate(trial_type_labs = case_when(trial_type == "pre-switch" ~ "Training",
                                     trial_type == "post-switch" ~ "Test")) %>%
  mutate(trial_type_labs = factor(trial_type_labs, levels = c("Training", "Test"))) %>%
  pivot_wider(names_from = AOI, values_from = Prop) %>%
  group_by(trial_type_labs, language, Time, trial_num) %>% 
  summarise(target = mean(target, na.rm=TRUE), 
            distractor = mean(distractor, na.rm=TRUE),
            circle = mean(circle, na.rm = TRUE)) %>%
  pivot_longer(cols = c(circle, target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
  mutate(aoi = factor(aoi, levels = c("circle", "target", "distractor")),
         trial_labels = paste0("Trial ", trial_num), 
         #setting up the layer for the transparent rectangle showing the anticipation period
         xmin = case_when(Time == 3000 & language == "Monolinguals" & aoi == "target" ~ 3150, 
         TRUE ~ 3000),
         xmax = case_when(Time == 3000 & language == "Monolinguals" & aoi == "target" ~ 4150, 
         TRUE ~ 3000),
         ymin = case_when(Time == 3000 & language == "Monolinguals" & aoi == "target" ~ Inf, 
         TRUE ~ 0),
         ymax = case_when(Time == 3000 & language == "Monolinguals" & aoi == "target" ~ -Inf,
         TRUE ~ 0)) %>% 
  ggplot(aes(x = Time, y = prop_looking, color = language, linetype = aoi)) + 
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = "Anticipation Period"), alpha = .1, colour = "transparent", show.legend = FALSE) +
  geom_line(aes(alpha = aoi, size = aoi)) +
  scale_color_manual(values = line_colors, guide = guide_legend(order = 1)) +
  scale_fill_manual(values = "#ffb600", labels = c("Anticipation Period"), guide = guide_legend(order = 3)) + 
  scale_linetype_manual(values = line_types, labels = c("Central fixation cue", "Target", "Distractor"), guide = guide_legend(order = 2)) +
  scale_y_continuous(n.breaks = 3) +
  scale_x_continuous(breaks = c(3000, 4000, 5000)) + 
  scale_alpha_manual(values = c(0.5, 0.9, 0.725), guide = "none") +
  scale_size_manual(values = line_sizes, guide = "none") +
  labs(linetype = "Area of interest",
       color = "Language group",
       fill = "Time period") +
  geom_text(data = facet_text, label = facet_text$label, show.legend = FALSE, color = "#666666",
            size = 3) +
  facet_grid(trial_labels ~ trial_type_labs) +
  ggtitle("Time course of infant looking for Study 1b") + 
  theme_minimal(base_size = 13.5) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#D9D9D9", color = "#9b9b9b"),
        panel.background = element_rect(fill = "transparent", color = "transparent"),
        panel.grid = element_line(color = "#eaeaea"),
        panel.grid.major = element_line(size = .25),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.spacing = unit(.5, "lines"),
        axis.text = element_text(size = 10)) +
  xlab("\nTime from trial start (ms)")  +
  ylab("Proportion looking\n") 

time_series_full_trial

ggsave("plot_time_series_full_trial_filter_v2.png", 
       path = here("03_output/02_re_analysis/"), 
       width = 9, height = 9, units = "in", dpi = 300) # 2700 x 2700 pixels 

###------------------------------------------PLOT ANTICIPATION PERIOD------------------------------------------

### These plots show accuracy over the course of trials, not time bins
time_series_antic <- 
  data_time_series_antic %>%
  pivot_wider(names_from = AOI, values_from = Prop) %>%
  group_by(trial_type, language, trial_num) %>%
  summarise(target = mean(target, na.rm=TRUE),
            distractor = mean(distractor, na.rm=TRUE)) %>%
  pivot_longer(cols = c(target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
  mutate(aoi = factor(aoi, levels = c("target", "distractor"))) %>%
  mutate(trial_labels = paste0("Trial ", trial_num)) %>%
  ggplot(aes(x = trial_num, y = prop_looking, color = language, linetype = aoi)) + 
  geom_smooth(se = FALSE) +
  facet_grid( ~ trial_type) +
  ggtitle("Time course of looking for Study 1b") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9)) +  
  xlab("Trial Number")  +
  ylab("Proportion looking")
 
time_series_antic
```

## Plot real data to compare w/ models

```{r model_with_time_bins, echo = FALSE}
blues_palette <- colorRampPalette(c("#C6DBEF", "#081D58"))
blues <- blues_palette(9)
  
tnum <- 
  data_time_series_antic %>%
  filter(AOI == "target") %>% 
  mutate(trial_num = factor(trial_num),
         trial_type = case_when(trial_type == "pre-switch" ~ "Training",
                                trial_type == "post-switch" ~ "Test"),
         trial_type = factor(trial_type, levels = c("Training", "Test"))) %>%
  group_by(TimeBin, trial_num, language, trial_type) %>%
  summarize(prop_looking = mean(Prop, na.rm = TRUE)) %>%
  ggplot(aes(x = as.numeric(TimeBin), y = prop_looking, color = trial_num)) +
  scale_color_manual(values = blues) +
  scale_x_continuous(labels = c(0, 250, 500, 750, 1000)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(language ~ trial_type) +
  labs(y = "Proportion looking", x = "Time from start of Anticipation Period (ms)") +
  ggtitle("Study 1b - D'Souza et al. (2020)") +
  theme(panel.grid.minor = element_blank())

tnum
```

# Model data

```{r}
model_data <- 
  data_time_series_antic %>%
  filter(AOI == "target",
         trial_num != 1) %>%
  mutate(trial_num_scaled = trial_num - 2)

model_data_pre <- 
  model_data %>%
  filter(trial_type == "pre-switch") 

model_data_post <-  
  model_data %>%
  filter(trial_type == "post-switch")
```


# Raw model data plots

```{r}
model_data_pre %>% 
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Pre-Switch")

model_data_post %>% 
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Post-Switch")
```


# Models

```{r}
###-------------------------------------------------------------PRE SWITCH --------------
###------------------------------------------------------------GLMER ----------------

glmermodel_pre <- 
  model_data_pre %>% 
  glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + (1 | id),
        data = ., 
        family = binomial, 
        weights = SamplesTotal, 
        control = glmerControl(optimizer="bobyqa", 
                               optCtrl = list(maxfun = 100000)))

final_model_pre <-  glmermodel_pre
  
summary(final_model_pre)

###-------------------------------------------------------------POST SWITCH --------------
###-------------------------------------------------------------GLMER ----------------
glmermodel_post <- 
  model_data_post %>% 
  glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + (1|id), 
        data = ., 
        family = binomial, 
        weights = SamplesTotal, 
        control = glmerControl(optimizer="bobyqa", 
                               optCtrl = list(maxfun = 100000)))

final_model_post <- glmermodel_post

summary(final_model_post)

###----------------------------------------------------TABLE OF MODEL RESULTS-----------------

tab_model(final_model_pre, show.re.var = FALSE, show.icc = FALSE, 
          file = here("03_Output/02_re_analysis/glermodel_pre_dsouza_pruned_full_filter_v2.doc"))
tab_model(final_model_post, show.re.var = FALSE, show.icc = FALSE, 
          file = here("03_Output/02_re_analysis/glermodel_pos_dsouza_pruned_full_filter_v2.doc"))

###----------------------------------------------------PLOT OF MODEL RESULTS-----------------

ggpredict(final_model_pre, terms = c("TimeBin", "trial_num_scaled", "language"), type = "re", ci.lvl = FALSE) %>% 
  plot(colors = "trial_num_scaled", line.size = 1, connect.lines = TRUE) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \n in Study 1b", 
       x = "Time in milliseconds during anticipation period", 
       y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

ggsave("plot_model_dsouza_pre_glmer_filtered_v2.png", 
       path = here("03_output/02_re_analysis/"), 
       device = "png", width = 7, height = 4, units = "in", dpi = 300)


ggpredict(final_model_post, terms = c("TimeBin", "trial_num_scaled", "language"), type = "fe", ci.lvl = FALSE) %>% 
  plot(colors = "trial_num_scaled", line.size = 1, connect.lines = TRUE) +
  labs(title = "Predicted values of proportion looking to target during the Test phase \n in Study 1b", 
       x = "Time in milliseconds during anticipation period", 
       y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

ggsave("plot_model_dsouza_post_glmer_filtered_v2.png", 
       path = here("03_output/02_re_analysis/"), 
       device = "png", width = 7, height = 4, units = "in", dpi = 300)
```

# Correlation

Check if overall performance correlates across conditions

## Data

```{r}
corr_data <- 
  model_data %>% 
  group_by(trial_type, language, id) %>% 
  summarise(mean_prop = mean(Prop, na.rm = T)) %>% 
  ungroup()

corr_mono <- 
  corr_data %>% 
  filter(language == "Monolinguals") %>% 
  spread(key = trial_type, value = mean_prop)

corr_bi <- 
  corr_data %>% 
  filter(language == "Bilinguals") %>% 
  spread(key = trial_type, value = mean_prop)
```

## Model - Bilinguals

```{r}
###----------------------------------------------------Bilinguals -----------------
# package for visualization
library("ggpubr")

# correlations
cor(corr_bi$`pre-switch`, corr_bi$`post-switch`, method = "pearson")
cor.test(corr_bi$`pre-switch`, corr_bi$`post-switch`, method = "pearson")

# normality assumptions
shapiro.test(corr_bi$`pre-switch`) # 0.8168
shapiro.test(corr_bi$`post-switch`) # 0.1813
ggqqplot(corr_bi$`pre-switch`, ylab = "pre-switch")
ggqqplot(corr_bi$`post-switch`, ylab = "post-switch")

# visualization
ggscatter(corr_bi, x = "post-switch", y = "pre-switch", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "post-switch", ylab = "pre-switch")
```

## Model - Monolinguals

```{r}
###----------------------------------------------------Monolinguals -----------------
# correlations
cor(corr_mono$`pre-switch`, corr_mono$`post-switch`, method = "pearson")
cor.test(corr_mono$`pre-switch`, corr_mono$`post-switch`, method = "pearson")

# normality assumptions
shapiro.test(corr_mono$`pre-switch`) # 0.003
shapiro.test(corr_mono$`post-switch`) # 0.0001
ggqqplot(corr_mono$`pre-switch`, ylab = "pre-switch")
ggqqplot(corr_mono$`post-switch`, ylab = "post-switch")

# visualization
ggscatter(corr_mono, x = "post-switch", y = "pre-switch", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "post-switch", ylab = "pre-switch")
```
