---
title: "CogControl Results"
output: html_notebook
---

## Clear workspace and load packages
```{r}

## Clear workspace
rm(list = ls())

## Load packages
library(tidyverse)
library(readxl)
library(stringr)
library(tidyr)
#library(car)
library(ez)


```

## Define minimum looking and minimum trial numbers for this study
```{r, echo = FALSE}

MIN_LOOK_PROPORTION <- .5
MIN_NUMBER_TRIALS <- 5

```


## Read in data
```{r, echo = FALSE}

## Read tobii data 
  Mydata <- read_excel("../data/tobii.June10th.xlsx", na="-")

 #Read in master_subject_list 
  participants <- read_excel("../data/mslist.xlsx", na="-") %>%
  separate(lang.group,into = c("language", "group")) %>%
  filter(keeper == 1) 
  
```

## Prep participant dataframe

```{r, echo = FALSE}
## Change data types to proper ones
participants <- participants %>%  
  mutate(age.group = fct_rev(as.factor(age.group))) %>%
  rename(age_group = age.group) %>%
  mutate(language = fct_rev(as.factor(language))) %>%
  mutate(total.vocab.prod = as.numeric(total.vocab.prod)) %>%
  mutate(total.concept.prod = as.numeric(total.concept.prod)) %>%
  mutate(recording.name = as.factor(recording.name)) %>%
  mutate(gender = as.factor(gender)) %>%
  group_by(language) %>%
  mutate(median.byGroup= median(total.concept.prod,na.rm=T)) %>%
  mutate(vocab_group = ifelse(median.byGroup>total.concept.prod,
                             "Low", 
                             "High")) %>%
  mutate(vocab_group = as.factor(vocab_group)) 

```



## Fix column names and substitute 0 for NAs in eyetracking data
```{r, echo = FALSE}

names(Mydata) <- gsub("Total Fixation Duration_Test", "Test", names(Mydata))
names(Mydata) <- gsub("Total Fixation Duration_Training", "Training", names(Mydata))
names(Mydata) <- gsub("Circle_Sum", "Circle", names(Mydata))
names(Mydata) <- gsub("Target_Sum", "Target", names(Mydata))
names(Mydata) <- gsub("Distractor_Sum", "Distractor", names(Mydata))
names(Mydata) <- gsub("Test", "Test_", names(Mydata))
names(Mydata) <- gsub("Training", "Training_", names(Mydata))

Mydata[is.na(Mydata)] <- 0 

Mydata$recording.name = as.factor(Mydata$recording.name) # Make recording name a factor

```

## Wrangle to create analyzable data set
```{r, echo = FALSE}

trial_data_set <- Mydata %>%
  
## Convert data from wide to long, and then from long to wide
  select(recording.name, contains("Circle"), contains("Distractor"), contains("Target")) %>%
  gather(AOI, looking_time, Test_1_Circle:Training_9_Target) %>%
  separate(AOI,into = c("trial_type", "trial_number", "AOI")) %>%
  spread(AOI, looking_time) %>%
  
## Change to proper variable types and rename variables
    mutate(trial_type = fct_rev(as.factor(trial_type))) %>%
    mutate(trial_number = as.numeric(trial_number)) %>%
   mutate(trial_type = dplyr::recode(trial_type, "Test" = "post-switch", "Training" = "pre-switch")) %>%
  
## Calculate total looking time
  mutate(All_looking_time = Circle + Distractor + Target) %>%
  
## Determine whether baby was attending during minimum proportion of anticipatory period
  mutate(good_trial = ifelse(All_looking_time >= `MIN_LOOK_PROPORTION`, "good", "bad")) %>%
  filter(good_trial == "good") %>% 
  group_by(recording.name, trial_type) %>% 
  mutate(num_good_trial = length(recording.name)) %>%

## determine whether baby had the minimum bumber of good trials  
  filter(num_good_trial >= `MIN_NUMBER_TRIALS`) %>%
  group_by(recording.name) %>% 
  mutate(good_baby = length(unique(trial_type))) %>%
  filter(good_baby == 2) %>%
  
##categorizing trials as correct, incorrect, or no anticipation
  mutate(correct_anticipation = ifelse(Target > Distractor, 1, 0)) %>%
  mutate(incorrect_anticipation = ifelse(Distractor > Target, 1, 0)) %>%
  mutate(no_anticipation = ifelse(Target + Distractor == 0, 1, 0)) %>%
  mutate(all_anticipation = 1-no_anticipation) %>%
  mutate(prop_correct_anticipation = Target/(Target+Distractor)) 
```

## merge data_set with master.subject.list
```{r}

trial_data_all <- merge(trial_data_set, participants, by="recording.name") 
```

## Check the number of keeper participants in each group
```{r}

trial_data_all %>%
  group_by(age_group, language) %>%
  summarize(num_participants = length(unique(recording.name)))

```

## Only including trials with any anticipation
```{r}
trial_data <- trial_data_all %>%
  filter(no_anticipation == 0)


```



## Anticipations by block, including only trials with anticipations
```{r, echo = FALSE}
block_data <- trial_data_all %>%
  mutate(block_num = (as.numeric(trial_number)+2) %/% 3) %>%
  filter(no_anticipation == 0) %>%
  group_by(recording.name, language, 
           trial_type, block_num, age_group, vocab_group) %>%
  rename(cor_anticipation = correct_anticipation) %>%
  summarise(num_trials_contributed = length(cor_anticipation), correct_anticipation = mean(cor_anticipation,na.rm=T)) %>%
  group_by(recording.name, trial_type) %>%
  mutate(n_blocks = length(unique(block_num))) %>%
  mutate(block_num = as.factor(block_num))
  
  
```

## Show block means by group and trial type
```{r}

block_data %>%
  group_by(language, age_group, trial_type, block_num) %>%
  summarise(correct_anticipation = mean(correct_anticipation), num_trials_contributed = mean(num_trials_contributed))

```



## Plot results by trial

```{r}

trial_figure <- trial_data %>%
  ggplot(aes(x = trial_number, y = correct_anticipation, color = language, shape =language, linetype = language)) +
  stat_summary(fun.y = "mean", geom = "point") +
  stat_smooth(se = FALSE) +
  facet_grid(age_group ~ trial_type) +
  scale_x_discrete(limits = c(1:9)) +
  scale_y_continuous(limits = c(0:1)) +
  theme_bw(base_size=22) +
  scale_color_manual(values = c("#ff3300", # bilingual colour
                                "#070707")) + # mono colour
    xlab("Trial number") +
  ylab("Proportion correct anticipation")

trial_figure

#ggsave("../figures/CogControl_trials.pdf", trial_figure, device = "pdf")

```


## Plot results by block

```{r}
blocks_figure <- block_data %>%
  ggplot(aes(x = block_num, y = correct_anticipation, fill = language)) +
  stat_summary(fun.y = "mean", geom = "bar", position = "dodge") +
  facet_grid(age_group ~ trial_type) +
  scale_y_continuous(limits = c(0:1)) +
  theme_bw(base_size=22) +
  scale_color_manual(values = c("#ff3300", # bilingual colour
                                "#070707")) + # mono colour
  xlab("Block number") +
  ylab("Proportion correct anticipation")

blocks_figure
```


## ANOVA by block: 7m pre-switch
```{r}

#ezDesign(block_data, y = recording.name, x = block_num, row = trial_type)


pre_7 <- block_data %>%
    filter(age_group == "7 months") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            between = language, 
            detailed = TRUE,
            type = 3)
  
pre_7_mono <-  block_data %>%
    filter(age_group == "7 months") %>%
    filter(language == "Monolinguals") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)
  
pre_7_bi <-  block_data %>%
    filter(age_group == "7 months") %>%
    filter(language == "Bilinguals") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)


  
```



## ANOVA by block: 7m post-switch
```{r}

#ezDesign(block_data, y = recording.name, x = block_num, row = trial_type)


post_7 <- block_data %>%
    filter(age_group == "7 months") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            between = language, 
            detailed = TRUE,
            type = 3)
  
post_7_mono <-  block_data %>%
    filter(age_group == "7 months") %>%
    filter(language == "Monolinguals") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)
  
post_7_bi <-  block_data %>%
    filter(age_group == "7 months") %>%
    filter(language == "Bilinguals") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)


  
```



## ANOVA by block: 20m pre-switch
```{r}

#ezDesign(block_data, y = recording.name, x = block_num, row = trial_type)


pre_20 <- block_data %>%
    filter(age_group == "20 months") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            between = language, 
            detailed = TRUE,
            type = 3)
  
pre_20_mono <-  block_data %>%
    filter(age_group == "20 months") %>%
    filter(language == "Monolinguals") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)
  
pre_20_bi <-  block_data %>%
    filter(age_group == "20 months") %>%
    filter(language == "Bilinguals") %>%
    filter(trial_type == "pre-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)


  
```



## ANOVA by block: 20m post-switch
```{r}

#ezDesign(block_data, y = recording.name, x = block_num, row = trial_type)


post_20 <- block_data %>%
    filter(age_group == "20 months") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            between = language, 
            detailed = TRUE,
            type = 3)
  
post_20_mono <-  block_data %>%
    filter(age_group == "20 months") %>%
    filter(language == "Monolinguals") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)
  
post_20_bi <-  block_data %>%
    filter(age_group == "20 months") %>%
    filter(language == "Bilinguals") %>%
    filter(trial_type == "post-switch") %>%
    filter(n_blocks == 3) %>%
    ezANOVA(data = ., 
            dv = correct_anticipation,
            wid = recording.name,
            within = block_num,
            detailed = TRUE,
            type = 3)


  
```


## t-tests compared to chance by trial type, block, language group, age group
```{r}

block_data %>%
  filter(age_group != "20 months" | language != "Bilinguals" | trial_type != "pre-switch" | block_num != 3) %>% # No variability in this cell - all 1
  group_by(age_group, language, trial_type, block_num) %>%
  do(broom::tidy(t.test(.$correct_anticipation, mu = .5, data = .))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) %>%
  mutate_if(is.numeric, funs(round(., 3)))

```


## t-tests comparing Blocks 1 and 3, by trial type, language group, age group
```{r}

block_data %>%
  filter(block_num !=2) %>%
  group_by(recording.name, age_group, language, trial_type) %>%
  mutate(n_blocks = length(block_num)) %>%
  filter(n_blocks == 2) %>%
  group_by(age_group, language, trial_type) %>%
   do(broom::tidy(t.test(.$correct_anticipation ~ .$block_num, data = ., paired = TRUE))) %>%
  mutate(cohen_d = statistic/sqrt(parameter +1)) %>%
  mutate_if(is.numeric, funs(round(., 3)))

```


```{r}

trial_data %>%
  filter(age_group == "20 months" & trial_number == 2 & trial_type == "post-switch") %>%
  do(broom::tidy(t.test(.$correct_anticipation ~ .$language, data = ., paired = FALSE)))

```


