---
title: "raw_data_analysis"
author: "Hilary Killam"
date: "January 27, 2020"
output: html_document
---
##Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## Load packages
library(tidyverse)
library(readxl)
library(stringr)
library(tidyr)
library(ggplot2)
library(car)
library(ez)
library(snakecase)
library(janitor)
library(lme4)
library(effects)
library(emmeans)
library(apaTables)
library(here)
library(eyetrackingR)
library(patchwork)
library(ggeffects)
library(interactions)
library(gt)
library(flextable)
library(grDevices)
library(apa)
library(sjPlot)
options(scipen = 999)

kovacs09 <- "Kovács & Mehler 2009"

## Define minimum looking and minimum trial numbers for this study
MIN_LOOK_PROPORTION <- .5
MIN_NUMBER_TRIALS <- 5

```

##Load Data

```{r load_data, include = FALSE}

###------------------------------------------------------LOAD DATA-------------------------------------------------

#Full Trials (with final sample only - excluded babies already removed in load and merge script)
load(here("data", "data_full_trials.Rda"))

#Master Subject List (with final sample only - excluded babies already removed in load and merge script)
load(here("data", "final_sample_mslist.Rda"))

#Anticipation period of trials (with final sample only - excluded babies already removed in load and merge script)
load(here("data", "data_anticipation.Rda"))

#Exclusion data (includes everyone -- excluded and included)
load(here("data", "exclusions.Rda"))

OVERALL_VOCAB_MEDIAN <- final_sample_mslist %>%
  filter(age_group == "20 months") %>%
  summarize(median = median(cdi_tot_vocab_prod, na.rm = TRUE)) %>%
  pull(median)

```


##Descriptives

```{r descriptives, echo = FALSE}

###------------------------------------------------FINAL SAMPLE COUNTS PER AGE--------------------------------------

final_sample_mslist %>%
  group_by(age_group) %>%
  summarize(count = length(unique(recording_name)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            num_female = sum(gender == 1))
  

###------------------------------------------------FINAL SAMPLE COUNTS PER GROUP--------------------------------------

final_sample_mslist %>%
  group_by(language, age_group) %>%
  summarize(count = length(unique(recording_name)),
            vocab_median = median(cdi_tot_vocab_prod, na.rm = TRUE), 
            vocab_mean = mean(cdi_tot_vocab_prod, na.rm = TRUE),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            num_female = sum(gender == 1))

###-----------------------------------------------FINAL SAMPLE COUNTS PER VOCAB GROUP------------------------------

final_sample_mslist %>%
  filter(age_group == "20 months") %>%
  group_by(language, vocab_group) %>%
  summarize(count = length(unique(recording_name)),
            vocab_median = median(cdi_tot_vocab_prod, na.rm = TRUE), 
            vocab_mean = mean(cdi_tot_vocab_prod, na.rm = TRUE),
            avg_age_days = mean(total_age_days_excel, na.rm = TRUE),
            num_female = sum(gender == 1))

final_sample_mslist %>%
  filter(age_group == "20 months") %>%
  mutate(exclude = case_when(language == "Bilinguals" & is.na(cdi_prod_eng) ~ "exclude",
                             language == "Bilinguals" & is.na(cdi_prod_fr) ~ "exclude",
                             TRUE ~ "keep")) %>%
  filter(exclude == "keep") %>%
  group_by(language) %>%
  summarize(vocab_median = median(total_vocab_prod))
  

###-----------------------------------------------FINAL SAMPLE COUNTS PER LANG BACKGROUND------------------------------

final_sample_mslist %>%
  group_by(age_group, language, group) %>%
  summarize(count = length(unique(recording_name)))


###-----------------------------------------------FINAL SAMPLE COUNTS PER EXCLUSION REASON--------------------------

exclusions %>%
  count(age_group, excl_reason) %>%
  arrange(age_group, desc(n))

###----------------------------------------------------------COMPARE GROUPS------------------------------
summary_7 <- final_sample_mslist %>%
  filter(age_group == "7 months") 

summary_20 <- final_sample_mslist %>%
  filter(age_group == "20 months")

summary(summary_7$total_age_days_excel)
summary(summary_20$total_age_days_excel)

ggplot(summary_7, aes(total_age_days_excel)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~ language)

ggplot(summary_20, aes(total_age_days_excel)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~ language)

t.test(total_age_days_excel ~ language, data = summary_7) # no age diff between mono and bi 7 month olds
t.test(total_age_days_excel ~ language, data = summary_20) # no age diff between mono and bi 20 month olds

###----------------------------------------------------------COMPARE MATERNAL EDUCATION------------------------------

final_sample_mslist %>%
  mutate(mother_edu = case_when(is.na(mother_edu) ~ "other",
                                TRUE ~ mother_edu)) %>%
  group_by(age_group, language) %>%
  count(mother_edu) %>%
  mutate(pct = n/sum(n)) %>%
  arrange(age_group, language, desc(n))




```
##Language tables

```{r tables}
#--------------------------------------------Tried with gt package, looks terrible in RTF


# final_sample_mslist %>%
#   filter(age_group == "7 months" & language == "Bilinguals") %>%
#   select(recording_name, dom_lang, per_eng, per_fr, other_lang_1, per_other_1) %>%
#   pivot_longer(cols = c(per_eng, per_fr, per_other_1), names_to = "lang", values_to = "lang_percent") %>%
#   mutate(lang = str_remove(lang, "per_"),
#          lang = case_when(lang == "eng" ~ "English",
#                           lang == "fr" ~ "French",
#                           lang == "other_1" ~ other_lang_1,
#                           TRUE ~ "oops"),
#          lang = str_to_title(lang)) %>%
#   group_by(recording_name) %>%
#   mutate(lang_order = case_when(lang_percent == max(lang_percent) ~ "L1",
#                                 lang_percent == min(lang_percent) ~ "L3",
#                                 TRUE ~ "L2")) %>%
#   ungroup() %>%
#   mutate(lang_percent = paste0(lang, "_", lang_percent)) %>%
#   pivot_wider(names_from = lang_order, values_from = lang_percent, id_cols = "recording_name") %>%
#   separate(L1, into = c("L1", "L1_pct"), sep = "_") %>%
#   separate(L2, into = c("L2", "L2_pct"), sep = "_") %>%
#   separate(L3, into = c("L3", "L3_pct"), sep = "_") %>%
#   select(recording_name, L1, L1_pct, L2, L2_pct, L3, L3_pct) %>%
#   rename(`Domnant Languge` = L1,
#          `Non-Dominant Language` = L2,
#          `Third Language` = L3,
#          `% 1` = L1_pct,
#          `% 2` = L2_pct,
#          `% 3` = L3_pct) %>%
#   mutate(id = row_number(),
#          `Third Language` = case_when(`% 3` == "0" ~ "",
#                                       TRUE ~ `Third Language`),
#          `% 3` = case_when(`% 3` == "0" ~ "",
#                            TRUE ~ `% 3`)) %>%
#   select(-recording_name) %>%
#   select(`Participant` = id, 1:6) %>%
#   gt() %>%
#   tab_header(title = md("*Language pairs spoken to bilinguals in Experiment 1 (7-month-olds)*")) %>%
#   tab_spanner(label = "Dominant Language", columns = vars(`Domnant Languge`, `% 1`)) %>%
#   tab_spanner(label = "Non-Dominant Language", columns = vars(`Non-Dominant Language`, `% 2`)) %>%
#   tab_spanner(label = "Third Language", columns = vars(`Third Language`, `% 3`)) %>%
#   cols_label(`Domnant Languge` = "language",
#              `Non-Dominant Language` = "language",
#              `Third Language` = "language",
#              `% 1` = "%",
#              `% 2` = "%",
#              `% 3` = "%") %>%
#   tab_style(style = list(cell_borders(sides = "all", weight = px(0))),
#             locations = cells_body()) %>%
#   tab_style(style = list(cell_text(font = "Times", align = "left")),
#            locations = list(cells_body(), 
#                             cells_title(),
#                             cells_column_labels(columns = 1:7),
#                             cells_column_spanners(spanners = c("Dominant Language", "Non-Dominant Language", "Third Language")))) %>%
#   tab_style(style = list(cell_text(size = 18, align = "left")),
#             locations = cells_title()) %>%
#   tab_options(table.width = px(750)) %>%
#   gtsave("part_lang_7.html")
  
#--------------------------------------------------------------------------------Flextable has a better result


##---------------------------------------------------------------------7 month old Table 1
final_sample_mslist %>%
  filter(age_group == "7 months" & language == "Bilinguals") %>%
  select(recording_name, dom_lang, per_eng, per_fr, other_lang1, per_other1) %>%
  pivot_longer(cols = c(per_eng, per_fr, per_other1), names_to = "lang", values_to = "lang_percent") %>%
  mutate(lang = str_remove(lang, "per_"),
         lang = case_when(lang == "eng" ~ "English",
                          lang == "fr" ~ "French",
                          lang == "other_1" ~ other_lang1,
                          TRUE ~ "oops"),
         lang = str_to_title(lang)) %>%
  group_by(recording_name) %>%
  mutate(lang_order = case_when(lang_percent == max(lang_percent) ~ "L1",
                                lang_percent == min(lang_percent) ~ "L3",
                                TRUE ~ "L2")) %>%
  ungroup() %>%
  mutate(lang_percent = paste0(lang, "_", lang_percent)) %>%
  pivot_wider(names_from = lang_order, values_from = lang_percent, id_cols = "recording_name") %>%
  separate(L1, into = c("L1", "L1_pct"), sep = "_") %>%
  separate(L2, into = c("L2", "L2_pct"), sep = "_") %>%
  separate(L3, into = c("L3", "L3_pct"), sep = "_") %>%
  select(recording_name, L1, L1_pct, L2, L2_pct, L3, L3_pct) %>%
  rename(`Domnant Languge` = L1,
         `Non-Dominant Language` = L2,
         `Third Language` = L3,
         `% 1` = L1_pct,
         `% 2` = L2_pct,
         `% 3` = L3_pct) %>%
  mutate(id = row_number(),
         `Third Language` = case_when(`% 3` == "0" ~ "",
                                      TRUE ~ `Third Language`),
         `% 3` = case_when(`% 3` == "0" ~ "",
                           TRUE ~ `% 3`)) %>%
  select(-recording_name) %>%
  select(`Participant` = id, 1:6) %>%
  flextable() %>%
  set_header_labels(`Domnant Languge` = "language",
             `Non-Dominant Language` = "language",
             `Third Language` = "language",
             `% 1` = "%",
             `% 2` = "%",
             `% 3` = "%") %>%
  add_header_row(values = c("", "Dominant Language", "Non-Dominant Language", "Third Language"), colwidths = c(1, 2, 2, 2)) %>%
  autofit() %>%
  add_header_lines(values = "Language pairs spoken to bilinguals in Experiment 1 (7-month-olds)") %>%
  font(fontname = "Times", part = "all") %>%
  fontsize(size = 12, part = "all") %>%
  italic(i = 1, part = "header") #################delete comment to save %>%
  #save_as_docx(path = "table_lang_7.docx")

#---------------------------------------------------------------------20 month old Table 2

final_sample_mslist %>%
  filter(age_group == "20 months" & language == "Bilinguals") %>%
  select(recording_name, dom_lang, per_eng, per_fr, other_lang1, per_other1) %>%
  pivot_longer(cols = c(per_eng, per_fr, per_other1), names_to = "lang", values_to = "lang_percent") %>%
  mutate(lang = str_remove(lang, "per_"),
         lang = case_when(lang == "eng" ~ "English",
                          lang == "fr" ~ "French",
                          lang == "other_1" ~ other_lang1,
                          TRUE ~ "oops"),
         lang = str_to_title(lang)) %>%
  group_by(recording_name) %>%
  mutate(lang_order = case_when(lang_percent == max(lang_percent) ~ "L1",
                                lang_percent == min(lang_percent) ~ "L3",
                                TRUE ~ "L2")) %>%
  ungroup() %>%
  mutate(lang_percent = paste0(lang, "_", lang_percent)) %>%
  pivot_wider(names_from = lang_order, values_from = lang_percent, id_cols = "recording_name") %>%
  separate(L1, into = c("L1", "L1_pct"), sep = "_") %>%
  separate(L2, into = c("L2", "L2_pct"), sep = "_") %>%
  separate(L3, into = c("L3", "L3_pct"), sep = "_") %>%
  select(recording_name, L1, L1_pct, L2, L2_pct, L3, L3_pct) %>%
  rename(`Domnant Languge` = L1,
         `Non-Dominant Language` = L2,
         `Third Language` = L3,
         `% 1` = L1_pct,
         `% 2` = L2_pct,
         `% 3` = L3_pct) %>%
  mutate(id = row_number(),
         `Third Language` = case_when(`% 3` == "0" ~ "",
                                      TRUE ~ `Third Language`),
         `% 3` = case_when(`% 3` == "0" ~ "",
                           TRUE ~ `% 3`)) %>%
  select(-recording_name) %>%
  select(`Participant` = id, 1:6) %>%
  flextable() %>%
  set_header_labels(`Domnant Languge` = "language",
             `Non-Dominant Language` = "language",
             `Third Language` = "language",
             `% 1` = "%",
             `% 2` = "%",
             `% 3` = "%") %>%
  add_header_row(values = c("", "Dominant Language", "Non-Dominant Language", "Third Language"), colwidths = c(1, 2, 2, 2)) %>%
  autofit() %>%
  add_header_lines(values = "Language pairs spoken to bilinguals in Experiment 2 (20-month-olds)") %>%
  font(fontname = "Times", part = "all") %>%
  fontsize(size = 12, part = "all") %>%
  italic(i = 1, part = "header") #################%>%
 # save_as_docx(path = "table_lang_20.docx")

#----------------------------------------------------Noticed in tables, some pcts don't add to 100

final_sample_mslist %>%
  mutate(total_lang_pct = per_eng + per_fr + per_other1 + per_other2) %>%
  select(recording_name, per_eng, per_fr, per_other1, per_other2, total_lang_pct) %>%
  filter(total_lang_pct != 100)

```


##EyetrackingR Data

```{r eyetrackingR_data, echo = FALSE}

###----------------------------------------------------CREATE EYETRACKINGR DATA FOR FULL TRIAL PLOTS

data_eyetracking_full_trials <- make_eyetrackingr_data(data_full_trials, 
                                participant_column = "recording_name",
                                trial_column = "trial_name", 
                                time_column = "trial_from_zero",
                                trackloss_column = "trackloss",
                                aoi_columns = c('target', 'circle', 'distractor'), # this will calculate prop looking in relation to all AOIs, not just target vs distractor. When I remove circle from here, the plot gets very wonky (I guess because of dividing by 0 in some cases?)
                                treat_non_aoi_looks_as_missing = TRUE)

full_trial_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 0,
                                     window_end_time = 5000, rezero = TRUE, remove = TRUE)

data_time_series_full <- make_time_sequence_data(full_trial_window,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "age_group", "cdi_tot_vocab_prod", "vocab_group", "vocab_centred", "vocab_scaled", "trial_type", "trial_num"),
                                         aois = c("circle", "target", "distractor"))

###---------------------------------------------CREATE EYETRACKINGR DATA FOR ANTICIPATION PERIOD PLOTS

data_eyetracking_antic_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 2150,
                                     window_end_time = 3150, rezero = TRUE, remove = TRUE)

trackloss <- trackloss_analysis(data = data_eyetracking_antic_window)

data_eyetracking_clean <- clean_by_trackloss(data = data_eyetracking_antic_window, trial_prop_thresh = .5) #this eliminates all data from trials with 50% or more trackloss (we merged the baby IDs who made it through to the final sample back with the full data, so makes sense we will re-exclude some trials here)

data_eyetracking_clean_nocircle <- make_eyetrackingr_data(data_full_trials, 
                                participant_column = "recording_name",
                                trial_column = "trial_name", 
                                time_column = "trial_from_zero",
                                trackloss_column = "trackloss",
                                aoi_columns = c('target', 'distractor'), # this will calculate prop looking in relation to just target vs distractor
                                treat_non_aoi_looks_as_missing = TRUE) %>%
  subset_by_window(window_start_time = 2150,
                   window_end_time = 3150, rezero = TRUE, remove = TRUE) %>%
  clean_by_trackloss(trial_prop_thresh = .5)

data_time_series_antic <- make_time_sequence_data(data_eyetracking_clean,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "age_group", "cdi_tot_vocab_prod", "vocab_group", "vocab_centred", "vocab_scaled", "trial_type", "trial_num"),
                                         aois = c("circle", "target", "distractor"))

```
##Time Series Plots

```{r time_series_plots, echo = FALSE}

#--------------------------------------------EyetrackingR Plots - not as flexible as ggplot so will try below with ggplot
# plot7_full_trial <- data_time_series %>%
#   filter(age_group == "7 months") %>%
#   plot(predictor_column = "trial_type")
# 
# plot7_full_trial
# 
# plot20_full_trial <- data_time_series %>%
#   filter(age_group == "20 months") %>%
#   plot(predictor_column = "trial_type")
# 
# plot20_full_trial

###----------------------------------------------------------PLOT FULL TRIALS-----------------------------------------
#line_colors <- c("#D7D7D7", "#FF3366", "#04BDD8")
#line_colors <- c("#D7D7D7", "#f77a6f", "#0485d6")
line_colors <- c("#f77a6f", "#016abf")
line_types <- c("dotted", "solid", "dashed")
line_sizes <- c(.6, 0.5, 0.5)
facet_text <- data.frame(trial_labels = c("Trial 1"), language = c("Monolinguals"), aoi = c("target"), Time = c(2650), trial_type_labs= c("Training", "Test"), prop_looking = c(.875), label = c("Anticipation period"))

time_series_full_trial <- data_time_series_full %>%
  filter(Time >= 1400 & Time <= 4000) %>%
  mutate(trial_type_labs = case_when(trial_type == "pre-switch" ~ "Training",
                                     trial_type == "post-switch" ~ "Test")) %>%
  mutate(trial_type_labs = factor(trial_type_labs, levels = c("Training", "Test"))) %>%
  pivot_wider(names_from = AOI, values_from = Prop) %>%
  group_by(trial_type_labs, language, age_group, Time, trial_num) %>%
  summarise(target = mean(target, na.rm=TRUE), 
            distractor = mean(distractor, na.rm=TRUE),
            circle = mean(circle, na.rm = TRUE))  %>%
  pivot_longer(cols = c(circle, target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
  mutate(aoi = factor(aoi, levels = c("circle", "target", "distractor")),
         trial_labels = paste0("Trial ", trial_num),
         xmin = case_when(Time == 2000 & language == "Monolinguals" & aoi == "target" ~ 2150, #setting up the layer for the transparent rectangle showing the anticipation period
         TRUE ~ 2000),
         xmax = case_when(Time == 2000 & language == "Monolinguals" & aoi == "target" ~ 3150,
         TRUE ~ 2000),
         ymin = case_when(Time == 2000 & language == "Monolinguals" & aoi == "target" ~ Inf,
         TRUE ~ 0),
         ymax = case_when(Time == 2000 & language == "Monolinguals" & aoi == "target" ~ -Inf,
         TRUE ~ 0),
         experiment = case_when(age_group == "7 months" ~ 1,
                                age_group == "20 months" ~ 2)) %>% 
  group_by(age_group) %>%
  nest() %>%
  #create nested data for easily plotting more than one of the same plot by a group
  mutate(plot = map2(data, age_group, ~ ggplot(data = .x, aes(x = Time, y = prop_looking, color = language, linetype = aoi)) + 
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = "Anticipation Period"), alpha = .1, colour = "transparent", show.legend = FALSE) +
  geom_line(aes(alpha = aoi, size = aoi)) +
  scale_color_manual(values = line_colors, guide = guide_legend(order = 1)) +
  scale_fill_manual(values = "#ffb600", labels = c("Anticipation Period"), guide = guide_legend(order = 3)) +
  scale_linetype_manual(values = line_types, labels = c("Central fixation cue", "Target", "Distractor"), guide = guide_legend(order = 2)) +
  scale_y_continuous(n.breaks = 3) +
  scale_x_continuous(breaks = c(2000, 3000, 4000)) +
  scale_alpha_manual(values = c(0.5, 0.9, 0.725), guide = "none") +
  scale_size_manual(values = line_sizes, guide = "none") +
  labs(linetype = "Area of interest",
       color = "Language group",
       fill = "Time period") +
  geom_text(data = facet_text, label = facet_text$label, show.legend = FALSE, color = "#666666", size = 3) +
  facet_grid(trial_labels ~ trial_type_labs) +
  # annotate("rect", xmin = 2150, xmax = 3150, ymin = -Inf, ymax = Inf, fill = "#fff000", alpha = 0.1) +
  # annotate("text", x = 2650, y = 0.875, label = "Anticipation \n Period", size = 2.75, color = "#927774") +
  ggtitle(paste0("Time course of infant looking for Experiment ", .$experiment, " (age ", age_group, ")")) +
  theme_minimal(base_size = 13.5) +
  theme(plot.title = element_text(hjust = 0.5),
        strip.background = element_rect(fill = "#D9D9D9", color = "#9b9b9b"),
        panel.background = element_rect(fill = "transparent", color = "transparent"),
        panel.grid = element_line(color = "#eaeaea"),
        panel.grid.major = element_line(size = .25),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.spacing = unit(.5, "lines"),
        axis.text = element_text(size = 10)) +
  xlab("\nTime from trial start (ms)")  +
  ylab("Proportion looking\n"))) 


# plot_ab <- data_time_series_full %>%
#   filter(Time >= 1500 & Time <= 3800) %>%
#   mutate(trial_type_labs = case_when(trial_type == "pre-switch" ~ "Training",
#                                      trial_type == "post-switch" ~ "Test")) %>%
#   mutate(trial_type_labs = factor(trial_type_labs, levels = c("Training", "Test"))) %>%
#   pivot_wider(names_from = AOI, values_from = Prop) %>%
#   group_by(trial_type_labs, language, age_group, Time, trial_num) %>%
#   summarise(target = mean(target, na.rm=TRUE), 
#             distractor = mean(distractor, na.rm=TRUE),
#             circle = mean(circle, na.rm = TRUE))  %>%
#   pivot_longer(cols = c(circle, target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
#   mutate(aoi = factor(aoi, levels = c("circle", "target", "distractor")))  %>%
#   mutate(trial_labels = paste0("Trial ", trial_num)) %>%
#   group_by(age_group) %>%
#   nest() %>%
#   #create nested data for easily plotting more than one of the same plot by a group
#   mutate(plot = map2(data, age_group, ~ ggplot(data = .x, aes(x = Time, y = prop_looking, color = aoi, linetype = language)) + 
#   geom_line(show.legend = FALSE) +
#   scale_color_manual(values = line_colors) +
#   facet_grid(trial_labels ~ trial_type_labs) +
#   annotate("rect", xmin = 2150, xmax = 3150, ymin = -Inf, ymax = Inf, fill = "red", alpha = 0.07) +
#   annotate("text", x = 2650, y = 0.9, label = "Anticipation \n Period", size = 2.5, color = "#927774") +
#   ggtitle(age_group) +
#   theme_minimal() +
#   theme(plot.title = element_text(hjust = 0.5), legend.title = element_blank(), axis.text.x = element_text(angle = 25, size = 8)) +
#   xlab("Time from trial start (ms)")  +
#   ylab("Proportion looking")))
  
plot_full_7 <- time_series_full_trial$plot[[1]] 
plot_full_20 <- time_series_full_trial$plot[[2]] 

# ggsave("plot_full_trial_7.2.png", path = here("figures"), plot = time_series_full_trial$plot[[1]], device = "png", width = 9, height = 9, units = "in", dpi = 300)

# ggsave("plot_full_trial_20.2.png", path = here("figures"), plot = time_series_full_trial$plot[[2]], device = "png", width = 9, height = 9, units = "in", dpi = 300)


###------------------------------------------PLOT ANTICIPATION PERIOD------------------------------------------

### These plots show accuracy over the course of trials, not time bins

time_series_antic <- data_time_series_antic %>%
  pivot_wider(names_from = AOI, values_from = Prop) %>%
  group_by(trial_type, language, age_group, trial_num) %>%
  summarise(target = mean(target, na.rm=TRUE),
            distractor = mean(distractor, na.rm=TRUE)) %>%
  pivot_longer(cols = c(target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
  mutate(aoi = factor(aoi, levels = c("target", "distractor"))) %>%
  mutate(trial_labels = paste0("Trial ", trial_num)) %>%
  group_by(age_group) %>%
  nest() %>%
  mutate(plot_all = map2(data, age_group, ~ ggplot(data = .x, aes(x = trial_num, y = prop_looking, color = language, linetype = aoi)) + 
  geom_smooth(se = FALSE) +
  facet_grid( ~ trial_type) +
  ggtitle(age_group) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9)) +  
  xlab("Trial Number")  +
  ylab("Proportion looking")))
  
plot_anticipation_7 <- time_series_antic$plot_all[[1]]
plot_anticipation_20 <- time_series_antic$plot_all[[2]]

#ggsave("antic_7_plot.png", plot = antic_7_plot, width = 15, height = 7, path = here("figures"))
#ggsave("antic_20_plot.png", plot = antic_20_plot, width = 15, height = 7, path = here("figures"))


###----------------------------------------PLOT ANTICIPATION PERIOD BY VOCAB GROUP--------------------------------

time_series_vocab <- data_time_series_antic %>%
  filter(age_group == "20 months") %>%
  pivot_wider(names_from = AOI, values_from = Prop) %>%
  group_by(trial_type, language, vocab_group, trial_num) %>%
  summarise(target = mean(target, na.rm=TRUE),
            distractor = mean(distractor, na.rm=TRUE))  %>%
  pivot_longer(cols = c(target, distractor), names_to = "aoi", values_to = "prop_looking") %>%
  mutate(aoi = factor(aoi, levels = c("target", "distractor")))  %>%
  mutate(trial_labels = paste0("Trial ", trial_num)) %>%
  ggplot(aes(x = trial_num, y = prop_looking, color = aoi, linetype = vocab_group)) + 
  geom_smooth(se = FALSE) +
  facet_grid(language ~ trial_type) +
  ggtitle("Proportion looking by vocab group (high/low) and language group") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9)) +  
  xlab("Trial Number") +
  ylab("Proportion looking")


```

##Plot vocab against accuracy

```{r}

###-----------------------------------------------------set vocab data - get rid of kids with incomplete cdi data
vocab_data <- data_time_series_antic %>%
  filter(age_group == "20 months" & !is.na(cdi_tot_vocab_prod))

##-------------------------------histogram of vocab scores for each language group
final_sample_mslist %>%
  filter(age_group == "20 months" & !is.na(cdi_tot_vocab_prod)) %>%
  ggplot(aes(x = cdi_tot_vocab_prod, fill = language)) +
  geom_histogram() +
  facet_wrap(~ language)

t.test(log(cdi_tot_vocab_prod) ~ language, data = vocab_data) # t test shows that the two groups' vocab distributions are not the same
  

#-------------------------------------plot vocab against accuracy by trial type & trial number
vocab_data %>%
  filter(AOI == "target") %>%
  group_by(recording_name, trial_num, trial_type, language, age_group, cdi_tot_vocab_prod, vocab_group) %>%
  summarize(Prop = mean(Prop, na.rm = TRUE)) %>%
  ggplot(aes(x = cdi_tot_vocab_prod, y = Prop, color = language)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_grid(trial_num ~ trial_type) +
  theme(legend.position = "bottom")


###------------------------------------same plot, but with 2 monolingual high vocab kids removed
vocab_data %>%
  filter(AOI == "target" & cdi_tot_vocab_prod < 300) %>%
  group_by(recording_name, trial_num, trial_type, language, age_group, cdi_tot_vocab_prod, vocab_group) %>%
  summarize(Prop = mean(Prop, na.rm = TRUE)) %>%
  ggplot(aes(x = cdi_tot_vocab_prod, y = Prop, color = language)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_grid(trial_num ~ trial_type) +
  theme(legend.position = "bottom")


```


## Plot real data to compare w/ models

```{r model_with_time_bins, echo = FALSE}
library(RColorBrewer)

blues_palette <- colorRampPalette(c("#C6DBEF", "#081D58"))
blues <- blues_palette(9)
  
tnum_7 <- data_time_series_antic %>%
  filter(age_group == "7 months",
         AOI == "target") %>%
  mutate(trial_num = factor(trial_num),
         trial_type = case_when(trial_type == "pre-switch" ~ "Training",
                                trial_type == "post-switch" ~ "Test"),
         trial_type = factor(trial_type, levels = c("Training", "Test"))) %>%
  group_by(TimeBin, trial_num, language, trial_type) %>%
  summarize(prop_looking = mean(Prop, na.rm = TRUE)) %>%
  ggplot(aes(x = as.numeric(TimeBin), y = prop_looking, color = trial_num)) +
  scale_color_manual(values = blues) +
  scale_x_continuous(labels = c(0, 250, 500, 750, 1000)) +
  #theme_dark() +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(language ~ trial_type) +
  labs(y = "Proportion looking", x = "Time from start of Anticipation Period (ms)") +
  ggtitle("7 months") +
  theme(panel.grid.minor = element_blank())

tnum_20 <- data_time_series_antic %>%
  filter(age_group == "20 months",
         AOI == "target") %>%
  mutate(trial_num = factor(trial_num)) %>%
  group_by(TimeBin, trial_num, language, trial_type) %>%
  summarize(prop_looking = mean(Prop, na.rm = TRUE)) %>%
  ggplot(aes(x = as.numeric(TimeBin), y = prop_looking, color = trial_num)) +
  scale_color_manual(values = blues) +
  #theme_dark() +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  coord_cartesian(ylim = c(0,1)) +
  facet_grid(language ~ trial_type) +
  ggtitle("20 months")
  
ggsave("trial_models_20.png", plot = tnum_20)

```


##Model data

```{r}

model_data <- data_time_series_antic %>%
  filter(AOI == "target",
         trial_num != 1) %>%
  mutate(trial_num_scaled = trial_num - 2)

model_data_7_pre <- model_data %>%
  filter(age_group == "7 months",
         trial_type == "pre-switch")

model_data_7_post <-  model_data %>%
  filter(age_group == "7 months",
         trial_type == "post-switch") 

model_data_20_pre <- model_data %>%
  filter(trial_type == "pre-switch",
         AOI == "target",
         !is.na(cdi_tot_vocab_prod)) %>%
  mutate(vocab_centred = as.numeric(vocab_centred),
         vocab_scaled = as.numeric(vocab_scaled))

model_data_20_post <- model_data %>%
  filter(trial_type == "post-switch",
         AOI == "target",
         !is.na(cdi_tot_vocab_prod)) %>%
  mutate(vocab_centred = as.numeric(vocab_centred),
         vocab_scaled = as.numeric(vocab_scaled))

```

## raw model data plots

For models, we want one data point per baby per trial to use (use made_time_window_data function)

each row from raw data is 1/60th of a second (60 Hz), approx. (added this to data but not sure what to do with it)
 
???? should there be a random slope for each participant by trial number?

```{r}
#plots with raw data points to compare to model prediction plots later

model_data_7_pre %>% ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Pre-Switch 7")
ggsave("plot_model_data_7pre.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)

model_data_7_post %>% ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Post-Switch 7")
ggsave("plot_model_data_7post.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)

model_data_20_pre %>% 
  mutate(vocab_grouped = case_when(vocab_centred <= -40 ~ "low",
                                   vocab_centred <= 40 ~ "middle",
                                   vocab_centred > 40 ~ "high"),
         vocab_grouped = factor(vocab_grouped, levels = c("low", "middle", "high"))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(aes(fill = cdi_tot_vocab_prod), alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid(vocab_grouped ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Pre-Switch 20")
ggsave("plot_model_data_20pre.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)

model_data_20_post %>%
  mutate(vocab_grouped = case_when(vocab_centred <= -40 ~ "low",
                                   vocab_centred <= 40 ~ "middle",
                                   vocab_centred > 40 ~ "high"),
         vocab_grouped = factor(vocab_grouped, levels = c("low", "middle", "high"))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(aes(fill = cdi_tot_vocab_prod), alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid(vocab_grouped ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  labs(color = "trial_num", title = "Post-Switch 20")
ggsave("plot_model_data_20post.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)

###-------------------------------Plot kid by kid, to see what's going on with vocab.... looks like 2 monolingual kids have high vocab scores and there are some trials with missing data, especially for post-switch

model_data_20_pre %>% 
  filter(language == "Monolinguals") %>%
  mutate(recording_name = fct_reorder(recording_name, desc(cdi_tot_vocab_prod))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = cdi_tot_vocab_prod)) + 
  geom_jitter() + 
  geom_smooth(se = FALSE) + 
  ggtitle("Monolinguals, Pre-Switch") +
  scale_color_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  facet_grid(recording_name ~ trial_num_scaled)

ggsave("plot_vocab_mono_20pre.png", path = here("figures"), device = "png", width = 7, height = 10, units = "in",
   dpi = 300)

model_data_20_pre %>% 
  filter(language == "Bilinguals" & !is.na(cdi_tot_vocab_prod)) %>%
  mutate(recording_name = fct_reorder(recording_name, desc(cdi_tot_vocab_prod))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = cdi_tot_vocab_prod)) + 
  geom_jitter() + 
  geom_smooth(se = FALSE) + 
  ggtitle("Bilinguals, Pre-Switch") +
  scale_color_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  facet_grid(recording_name ~ trial_num_scaled)

ggsave("plot_vocab_bi_20pre.png", path = here("figures"), device = "png", width = 7, height = 10, units = "in",
   dpi = 300)

model_data_20_post %>% 
  filter(language == "Monolinguals") %>%
  mutate(recording_name = fct_reorder(recording_name, desc(cdi_tot_vocab_prod))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = cdi_tot_vocab_prod)) + 
  geom_jitter() + 
  geom_smooth(se = FALSE) + 
  ggtitle("Monolinguals, Post-Switch") +
  scale_color_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  facet_grid(recording_name ~ trial_num_scaled)

ggsave("plot_vocab_mono_20post.png", path = here("figures"), device = "png", width = 7, height = 10, units = "in",
   dpi = 300)

model_data_20_post %>% 
  filter(language == "Bilinguals" & !is.na(cdi_tot_vocab_prod)) %>%
  mutate(recording_name = fct_reorder(recording_name, desc(cdi_tot_vocab_prod))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = cdi_tot_vocab_prod)) + 
  geom_jitter() + 
  geom_smooth(se = FALSE) + 
  ggtitle("Bilinguals, Post-Switch") +
  scale_color_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  facet_grid(recording_name ~ trial_num_scaled)

ggsave("plot_vocab_bi_20post.png", path = here("figures"), device = "png", width = 7, height = 10, units = "in",
   dpi = 300)

```

## models - 7 m
```{r}
###-------------------------------------------------------------PRE SWITCH 7 LMER--------------

#full model
lmermodel_7pre <- lmer(Prop ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_7_pre, REML = FALSE)
#without trial number
lmermodel_7pre2 <- lmer(Prop ~ language * TimeBin + (1 | recording_name), data = model_data_7_pre, REML = FALSE)
#without time bin
lmermodel_7pre3 <- lmer(Prop ~ language * trial_num_scaled + (1 | recording_name), data = model_data_7_pre, REML = FALSE)
#intercept only
lmermodel_7_prenull <- lmer(Prop ~ 1 + (1 | recording_name), data = model_data_7_pre, REML = FALSE)


summary(lmermodel_7pre) # AIC = 812.5
summary(lmermodel_7pre2) # AIC = 826.9
summary(lmermodel_7pre3) # AIC = 1220.9
summary(lmermodel_7_prenull) # AIC = 1229.7

###-------------------------------------------------------------COMPARE MODELS--------------

anova(lmermodel_7_prenull, lmermodel_7pre) # the full model is highly significantly better
anova(lmermodel_7pre, lmermodel_7pre2) # the full model is the best

###------------------------------------------------------------GLMER - MORE APPROPRIATE-----

glmermodel_7pre <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_7_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))) # nearly everything is significant in the glmer model

final_model_pre_7 <-  glmermodel_7pre
  
summary(final_model_pre_7)

###-------------------------------------------------------------POST SWITCH 7--------------

#full model
lmermodel_7post <- lmer(Prop ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_7_post, REML = FALSE)
#without trial number
lmermodel_7post2 <- lmer(Prop ~ language * TimeBin + (1 | recording_name), data = model_data_7_post, REML = FALSE)
#without time bin
lmermodel_7post3 <- lmer(Prop ~ language * trial_num_scaled + (1 | recording_name), data = model_data_7_post, REML = FALSE)
#intercept only
lmermodel_7_postnull <- lmer(Prop ~ 1 + (1 | recording_name), data = model_data_7_post, REML = FALSE)

summary(lmermodel_7post) # AIC = 411.5
summary(lmermodel_7post2) # AIC = 415.1
summary(lmermodel_7post3) # AIC = 576.9
summary(lmermodel_7_postnull) # AIC = 577.3

###-------------------------------------------------------------COMPARE MODELS--------------

anova(lmermodel_7_postnull, lmermodel_7post) # the full model is highly significantly better
anova(lmermodel_7post, lmermodel_7post2) # the full model is slightly significantly better

###-------------------------------------------------------------GLMER model--------------------

#glmer attempt
glmermodel_7post <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_7_post, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))) # nearly everything is significant in the glmer model

final_model_post_7 <- glmermodel_7post

summary(final_model_post_7)

###-------------------------------------------------------------ARE RESIDUALS NORMAL??--------------

hist(residuals(final_model_pre_7)) # slightly skewed
shapiro.test(residuals(final_model_pre_7)) # test says residuals are not normal
qqnorm(residuals(final_model_pre_7)) #qq plot looks okay
qqline(residuals(final_model_pre_7))

hist(residuals(final_model_post_7)) # slightly skewed
shapiro.test(residuals(final_model_post_7)) # test says residuals are not normal
qqnorm(residuals(final_model_post_7)) #qq plot is very wiggly 

###----------------------------------------------------TABLE OF MODEL RESULTS-----------------

tab_model(final_model_pre_7, show.re.var = FALSE, show.icc = FALSE)
tab_model(final_model_post_7, show.re.var = FALSE, show.icc = FALSE)

###----------------------------------------------------PLOT OF MODEL RESULTS-----------------

ggpredict(final_model_pre_7, terms = c("TimeBin", "trial_num_scaled", "language"), type = "re", ci.lvl = FALSE) %>% plot(colors = "trial_num_scaled", line.size = 1, connect.lines = TRUE) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \nin Experiment 1 (7 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

ggsave("plot_model_7_pre_glmer1.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)
 

ggpredict(final_model_post_7, terms = c("TimeBin", "trial_num_scaled", "language"), type = "fe", ci.lvl = FALSE) %>% plot(colors = "trial_num_scaled", line.size = 1, connect.lines = TRUE) +
  labs(title = "Predicted values of proportion looking to target during the Test phase \nin Experiment 1 (7 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

ggsave("plot_model_7_post_glmer1.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in",
   dpi = 300)
 
```



#models - 20 m
```{r}

###-------------------------------------------------------------PRE SWITCH 20--------------

lmermodel_20pre_novocab <- lmer(Prop ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_20_pre, REML = FALSE)

lmermodel_20pre <- lmer(Prop ~ language * vocab_centred * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_20_pre, REML = FALSE)

lmermodel_20pre.2 <- lmer(Prop ~ language * vocab_centred + (1 | recording_name), data = model_data_20_pre, REML = FALSE)

lmermodel_20pre.3 <- lmer(Prop ~ language * vocab_centred * TimeBin + (1 | recording_name), data = model_data_20_pre, REML = FALSE)


##---------------------------------------------------------------------MODEL SUMMARIES--------------

summary(lmermodel_20pre_novocab) #AIC = 1180.9
summary(lmermodel_20pre) #AIC = 1188.6
summary(lmermodel_20pre.2) #AIC = 1606.2
summary(lmermodel_20pre.3) #AIC = 1194.6

###-------------------------------------------------------------COMPARE MODELS--------------

anova(lmermodel_20pre_novocab, lmermodel_20pre) # no diff
anova(lmermodel_20pre.2, lmermodel_20pre) # need Time Bin
anova(lmermodel_20pre, lmermodel_20pre.3) # need trial num

###------------------------------------------------------------GLMER MODELS-----------------

glmermodel_20pre <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * vocab_scaled * trial_num_scaled + (trial_num_scaled | recording_name), data = model_data_20_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

glmermodel_20pre.2 <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + language * trial_num_scaled * vocab_scaled + (trial_num_scaled | recording_name), data = model_data_20_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

glmermodel_20pre.3 <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + language * trial_num_scaled * vocab_scaled + (1 | recording_name), data = model_data_20_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

tab_model(glmermodel_20pre.3, show.re.var = FALSE, show.icc = FALSE)

###-------------------------------------------------------------------FINAL MODEL-------------

final_model_pre_20 <- glmermodel_20pre.3

###-------------------------------------------------------------POST SWITCH 20--------------

lmermodel_20post_novocab <- lmer(Prop ~ language * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_20_post, REML = FALSE)

lmermodel_20post <- lmer(Prop ~ language * vocab_centred * TimeBin * trial_num_scaled + (1 | recording_name), data = model_data_20_post, REML = FALSE)

lmermodel_20post.2 <- lmer(Prop ~ language * vocab_centred + (1 | recording_name), data = model_data_20_post, REML = FALSE)

lmermodel_20post.3 <- lmer(Prop ~ language * vocab_centred * TimeBin + (1 | recording_name), data = model_data_20_post, REML = FALSE)

##---------------------------------------------------------------------MODEL SUMMARIES--------------

summary(lmermodel_20post_novocab) #AIC = 1269.2
summary(lmermodel_20post) #AIC = 1247.3
summary(lmermodel_20post.2) #AIC = 1470.5
summary(lmermodel_20post.3) #AIC = 1266.1

###-------------------------------------------------------------COMPARE MODELS--------------

anova(lmermodel_20post_novocab, lmermodel_20post) # with vocab is better
anova(lmermodel_20post, lmermodel_20post.2) # full model better
anova(lmermodel_20post, lmermodel_20post.3) # full model better


###--------------------------------------------------------------GLMER MODELS--------------

#glmer for comparison
glmermodel_20post <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * vocab_scaled * trial_num_scaled + (trial_num_scaled | recording_name), data = model_data_20_post, weights = SamplesTotal, family = binomial, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

glmermodel_20postnovocab <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + (trial_num_scaled | recording_name), data = model_data_20_post, weights = SamplesTotal, family = binomial, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

glmermodel_20post.2 <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + language * trial_num_scaled * vocab_scaled + (trial_num_scaled | recording_name), data = model_data_20_post, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

glmermodel_20post.3 <- glmer(SamplesInAOI / SamplesTotal ~ language * TimeBin * trial_num_scaled + language * trial_num_scaled * vocab_scaled + (1 | recording_name), data = model_data_20_post, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

tab_model(glmermodel_20post.3, show.re.var = FALSE, show.icc = FALSE)

###-------------------------------------------------------------------FINAL MODEL-------------

final_model_post_20 <- glmermodel_20post.3


###-------------------------------------------------------------ARE RESIDUALS NORMAL??--------------

hist(residuals(final_model_pre_20)) # slightly skewed
shapiro.test(residuals(final_model_pre_20)) # test says residuals are not normal
qqnorm(residuals(final_model_pre_20)) #qq plot looks okay

hist(residuals(final_model_post_20)) # slightly skewed
shapiro.test(residuals(final_model_post_20)) # test says residuals are not normal
qqnorm(residuals(final_model_post_20)) #qq plot is very wiggly 

###----------------------------------------------------TABLE OF MODEL RESULTS-----------------

tab_model(final_model_pre_20, show.re.var = FALSE, show.icc = FALSE)
tab_model(final_model_post_20, show.re.var = FALSE, show.icc = FALSE)

###----------------------------------------------------PLOT OF MODEL RESULTS - LMER-----------------

pre20predict <- ggpredict(glmermodel_20pre, terms = c("TimeBin", "trial_num_scaled", "language", "vocab_centred"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < -60 ~ "low vocab",
                           panel > 60 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

pre20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \nin Experiment 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

ggsave("plot_model_20_pre_glmer1.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in",
   dpi = 300)
 

post20predict <- ggpredict(glmermodel_20post, terms = c("TimeBin", "trial_num_scaled", "language", "vocab_scaled"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < 0 ~ "low vocab",
                           panel > .5 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

post20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \nin Experiment 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

ggsave("plot_model_20_post_glmer1.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in",
   dpi = 300)

##----------------------------------------------------------Predicted values plots GLMER------------

pre20predict <- ggpredict(glmermodel_20pre.3, terms = c("TimeBin", "trial_num_scaled", "language", "vocab_scaled"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < -.25 ~ "low vocab",
                           panel > .25 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

pre20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \nin Experiment 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

ggsave("plot_model_20_post_glmer1.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in",
   dpi = 300)

post20predict <- ggpredict(glmermodel_20post.3, terms = c("TimeBin", "trial_num_scaled", "language", "vocab_scaled"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < -.25 ~ "low vocab",
                           panel > .25 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

post20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Test phase \nin Experiment 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(0, 2, 4), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

ggsave("plot_model_20_post_glmer2.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in",
   dpi = 300)
```


##Block data

In `r kovacs09`, here is how they coded correct vs incorrect looks: 
>The screen was divided into 3 equal parts: left, middle, and right. We
coded infants’ anticipatory looks to the left or right side of the screen that
occurred during the 1-s time window starting 150 ms after the end of the word
and ending 150 ms after the appearance of the reward. These criteria were
based on previous studies (30–32). Trials in which the infant performed an
anticipatory look to the side where the puppet would appear were coded as
correct. If the infant did not look to the correct side during the anticipatory
period the trial was coded as incorrect. When infants looked both to the
correct and incorrect sides during the anticipatory period of the same trial, the
side of the longer look was coded. Taking the first look yields practically
identical data, given that in 94.8% of the trials infants looked to only one side.
As an additional analysis, we also coded perseverative looks in the postswitch
phase, that is, anticipatory looks to the location that had been valid previously.

So, correct is when TARGET is the only look, or the longest looking time
Incorrect is when the child did not look at the TARGET, or for less long than not


```{r block_data, echo = FALSE}

###---------------------------------------------------BLOCK DATA-------------------------------------------------------  

block_data <- data_eyetracking_clean %>%
  make_time_window_data(aois = c("target", "distractor", "circle"),
                        predictor_columns = c("age_group", "language", "cdi_tot_vocab_prod", "vocab_group", "trial_type", "trial_num")) %>%
  select(-Elog, -Weights, -LogitAdjusted, -ArcSin) %>%
  mutate(looking_ms = Prop * (SamplesTotal * (1000/60))) %>% #adds number of milliseconds spent looking at target for the trial
  pivot_wider(names_from = AOI, values_from = c(SamplesInAOI, Prop, looking_ms)) %>%
  mutate(total_looking_time = looking_ms_target + looking_ms_distractor + looking_ms_circle) %>%
  mutate(correct = case_when(looking_ms_target > looking_ms_distractor ~ 1, 
                                   TRUE ~ 0),
         incorrect = case_when(looking_ms_target < looking_ms_distractor ~ 1, 
                                     TRUE ~ 0),
         no_anticipation = case_when(looking_ms_target + looking_ms_distractor == 0 ~ 1, 
                              TRUE ~ 0),
         total_anticipation = 1 - no_anticipation) %>%
  #filter(no_anticipation == 0) %>% ### keep the circle looks!
  mutate(block_num = (as.numeric(trial_num)+2) %/% 3) %>%
  mutate(block_num = as.factor(block_num)) %>%
  group_by(recording_name, language, 
           trial_type, block_num, age_group, vocab_group, cdi_tot_vocab_prod) %>%
  summarise(num_trials_contributed = length(correct), 
            correct_anticipation = mean(correct, na.rm = TRUE),
            total_anticipation = mean(total_anticipation, na.rm = TRUE)) %>%
  group_by(recording_name, trial_type) %>%
  mutate(n_blocks = length(unique(block_num)),
         pooled_vocab_group = ifelse(OVERALL_VOCAB_MEDIAN > cdi_tot_vocab_prod,
                              "Low", 
                              "High"))

block_data_means <- block_data %>%
  group_by(language, age_group, trial_type, block_num) %>%
  summarise(correct_anticipation = mean(correct_anticipation), num_trials_contributed = mean(num_trials_contributed))

#-------------------------------------------------------check how many we lose who don't have 3 blocks of data---

block_data %>%
  group_by(age_group) %>%
  summarize(dropped = sum(n_blocks < 3))
  


replication_data <- data_eyetracking_clean %>%
  make_time_window_data(aois = c("target", "distractor", "circle"),
                        predictor_columns = c("age_group", "language", "total_vocab_prod", "vocab_group", "trial_type", "trial_num")) %>%
  select(-Elog, -Weights, -LogitAdjusted, -ArcSin) %>%
  mutate(looking_ms = Prop * (SamplesTotal * (1000/60))) %>% #adds number of milliseconds spent looking at target for the trial
  pivot_wider(names_from = AOI, values_from = c(SamplesInAOI, Prop, looking_ms)) %>%
  mutate(total_looking_time_wcircle = looking_ms_target + looking_ms_distractor + looking_ms_circle) %>%
  mutate(correct_wcircle = case_when(looking_ms_target > (looking_ms_distractor + looking_ms_circle) ~ 1, 
                                   TRUE ~ 0),
         incorrect_wcircle = case_when(looking_ms_target < (looking_ms_distractor + looking_ms_circle) ~ 1, 
                                     TRUE ~ 0),
         no_anticipation = case_when(looking_ms_target + looking_ms_distractor == 0 ~ 1, 
                              TRUE ~ 0),
         total_anticipation_wcircle = 1 - no_anticipation) %>%
  mutate(total_looking_time_nocircle = looking_ms_target + looking_ms_distractor,
         correct_nocircle = case_when(looking_ms_target > looking_ms_distractor ~ 1,
                                      TRUE ~ 0),
         incorrect_nocircle = case_when(looking_ms_target < looking_ms_distractor ~ 1,
                                        TRUE ~ 0)) %>%
  filter(no_anticipation == 0)

replication_data_plot_circle <- replication_data %>%
  ggplot(aes(x = trial_num, y = correct_wcircle, color = language)) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.05) +
  geom_smooth(se = FALSE) +
  facet_grid(age_group ~ trial_type) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9))

replication_data_plot_nocircle <- replication_data %>%
  ggplot(aes(x = trial_num, y = correct_nocircle, color = language)) +
  geom_jitter(alpha = 0.2, width = 0.1, height = 0.05) +
  geom_smooth(se = FALSE) +
  facet_grid(age_group ~ trial_type) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9))
```


#Anovas 7 m
```{r anovas}
#--------------------------------------------------------------------ANOVA by block: 7m pre-switch

pre_7 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  rename(language_group = language,
         block = block_num) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block,
          between = language_group, 
          detailed = TRUE,
          type = 3)
#-----------------------------------------------------------------make table
apa.ezANOVA.table(pre_7,
                  table.number = 3,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the training phase in Experiment 1 (7-month-olds)",
                  filename = here("figures", "anova_table_pre_7.doc"))

# aov_pre_7 <- block_data %>%
#   filter(age_group == "7 months") %>%
#   filter(trial_type == "pre-switch") %>%
#   filter(n_blocks == 3) %>%
#   aov(correct_anticipation ~ block_num*language + Error(recording_name/block_num), data = .)

#--------------------------------------------------------------------Monolingual pre switch

pre_7_mono <-  block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)
#--------------------------------------------------------------------T tests comparing improvement across blocks
pre_7_mono_t_1_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_7_mono_t_1_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_7_mono_t_2_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#--------------------------------------------------------------------Bilingual pre switch

pre_7_bi <-  block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)
#--------------------------------------------------------------------T tests comparing improvement across blocks

pre_7_bi_t_1_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_7_bi_t_1_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_7_bi_t_2_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#-------------------------------------------------------------------- T tests comparing mono to bi for each block

pre_7_t_1 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 1) %>%
  t.test(correct_anticipation ~ language, data = .)

pre_7_t_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 2) %>%
  t.test(correct_anticipation ~ language, data = .)

pre_7_t_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 3) %>%
  t.test(correct_anticipation ~ language, data = .)


#--------------------------------------------------------------------ANOVA by block: 7m post-switch

post_7 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          between = language, 
          detailed = TRUE,
          type = 3)

apa.ezANOVA.table(post_7,
                  table.number = 3,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the test phase in Experiment 1 (7-month-olds)",
                  filename = here("figures", "anova_table_post_7.doc"))

#-------------------------------------------------------------------- Monolinguals post switch

post_7_mono <-  block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

block_data %>%
  filter(age_group == "7 months" & trial_type == "post-switch" & n_blocks == 3) %>%
apa.2way.table(iv1 = block_num, 
               iv2 = language,
               dv = correct_anticipation, 
               data = ., 
               show.marginal.means = FALSE,
               filename = here("figures", "means_table_post_7.doc"), 
               table.number = 4)


#-------------------------------------------------------------------- T tests comparing mono improvement across blocks

post_7_mono_t_1_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

post_7_mono_t_1_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

post_7_mono_t_2_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#-------------------------------------------------------------------- Post switch bi

post_7_bi <-  block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)
#-------------------------------------------------------------------- T tests for bi improvement across blocks


post_7_bi_t_1_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

post_7_bi_t_1_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

post_7_bi_t_2_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#-------------------------------------------------------------------- T tests comparing mono to bi for each block


post_7_t_1 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(block_num == 1) %>%
  t.test(correct_anticipation ~ language, data = .) 

post_7_t_2 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(block_num == 2) %>%
  t.test(correct_anticipation ~ language, data = .)

post_7_t_3 <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(block_num == 3) %>%
  t.test(correct_anticipation ~ language, data = .)

t_table_7 <- broom::tidy(post_7_t_1) %>%
  bind_rows(broom::tidy(post_7_t_2)) %>%
  bind_rows(broom::tidy(post_7_t_3)) %>%
  rename(M_mono = estimate1,
         M_bi = estimate2,
         t = statistic,
         df = parameter) %>%
  select(-estimate, -method, -alternative)

#-------------------------------------------------------------------- Any difference in anticipations for 7 months?

pre_7_anticipations <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = total_anticipation,
          wid = recording_name,
          within = block_num,
          between = language, 
          detailed = TRUE,
          type = 3)

post_7_anticipations <- block_data %>%
  filter(age_group == "7 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = total_anticipation,
          wid = recording_name,
          within = block_num,
          between = language, 
          detailed = TRUE,
          type = 3)
```

#Anovas 20 m
```{r}

##---------------------------------------------------------------20 month pre switch
## ANOVA by block: 20m pre-switch


pre_20 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          between = .(language, pooled_vocab_group),
          detailed = TRUE,
          type = 3)

#-----------------------------------------------------------------make table
apa.ezANOVA.table(pre_20,
                  table.number = 6,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the training phase in Experiment 2 (20-month-olds)",
                  filename = here("figures", "anova_table_pre_20_pooled.doc"))

pre_20_mono <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

pre_20_bi <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)
#-----------------------------------------------------------------POST SWITCH 20

## ANOVA by block: 20m post-switch

post_20 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          between = .(language, pooled_vocab_group),
          detailed = TRUE,
          type = 3)

#-----------------------------------------------------------------make table
apa.ezANOVA.table(post_20,
                  table.number = 7,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the Test phase in Experiment 2 (20-month-olds)",
                  filename = here("figures", "anova_table_post_20_pooled.doc"))

post_20_mono <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

post_20_bi <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

```


