---
title: "Final Filtered Analyses"
author: "Hilary Killam"
date: "13/08/2020"
output: html_document
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

## Load packages
library(tidyverse)
library(readxl)
library(stringr)
library(tidyr)
library(ggplot2)
library(car)
library(ez)
library(snakecase)
library(janitor)
library(lme4)
library(effects)
library(emmeans)
library(apaTables)
library(here)
library(eyetrackingR)
library(patchwork)
library(ggeffects)
library(interactions)
library(gt)
library(flextable)
library(grDevices)
library(apa)
library(sjPlot)
options(scipen = 999)

kovacs09 <- "Kovács & Mehler 2009"

## Define minimum looking and minimum trial numbers for this study
MIN_LOOK_PROPORTION <- .5
MIN_NUMBER_TRIALS <- 5
TL_PROP <- 0.5

blues_palette <- colorRampPalette(c("#C6DBEF", "#081D58"))
blues <- blues_palette(9)

`%notin%` <- Negate(`%in%`)

```

#Load Data

```{r load_data, include = FALSE}

###------------------------------------------------------LOAD DATA-------------------------------------------------

#Full Trials (with final sample only - excluded babies already removed in load and merge script)
load(here("data", "data_full_trials.Rda"))

#Master Subject List (with final sample only - excluded babies already removed in load and merge script)
load(here("data", "final_sample_mslist.Rda"))

#fix one date of birth that is wrong in MSL
final_sample_mslist <- final_sample_mslist %>%
  mutate(do_birth = case_when(baby_id == 45798 ~ lubridate::ymd(20160924),
                              TRUE ~ lubridate::ymd(do_birth)),
         months = case_when(baby_id == 45798 ~ 20,
                            TRUE ~ months),
         days = case_when(baby_id == 45798 ~ 9,
                          TRUE ~ days),
         total_age_days_excel = case_when(baby_id == 45798 ~ 616,
                                          TRUE ~ total_age_days_excel)) %>% filter(age_group == "7 months" | (age_group == "20 months" & !is.na(cdi_tot_vocab_prod))) %>% #this MS list is to be used for vocabulary models for 20-month-olds
  filter(age_group == "20 months") 

data_full_trials <- final_sample_mslist %>%
  select(recording_name) %>%
  inner_join(data_full_trials, by = "recording_name")
  
#full MS list for cdi exclusions information

load(here("data", "ms_list_all.Rda"))

OVERALL_VOCAB_MEDIAN <- final_sample_mslist %>%
  summarize(median = median(cdi_tot_vocab_prod, na.rm = TRUE)) %>%
  pull(median)

```

#FINAL, FILTERED DATASET

##Descriptives

```{r descriptives, echo = FALSE}

###------------------------------------------------FINAL SAMPLE COUNTS PER AGE--------------------------------------

final_sample_mslist %>% 
  mutate(do_birth = lubridate::ymd(do_birth),
         do_participation = lubridate::ymd(do_participation),
         age_interval = lubridate::interval(do_birth, do_participation),
         age_total = lubridate::as.period(age_interval),
         years = lubridate::year(age_total),
         months = lubridate::month(age_total),
         days = lubridate::day(age_total),
         months = years*12 + months) %>%
  select(-age_interval, -age_total, -years) %>%
  group_by(age_group) %>%
  summarize(count = length(unique(recording_name)),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender == 1)) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)
  

###------------------------------------------------FINAL SAMPLE COUNTS PER GROUP--------------------------------------

final_sample_mslist %>% 
  group_by(language, age_group) %>%
  summarize(count = length(unique(recording_name)),
            vocab_median = median(cdi_tot_vocab_prod, na.rm = TRUE), 
            vocab_mean = mean(cdi_tot_vocab_prod, na.rm = TRUE),
            avg_age_days = floor(mean(total_age_days_excel, na.rm = TRUE)),
            min_age_days = min(total_age_days_excel),
            max_age_days = max(total_age_days_excel),
            avg_age = avg_age_days/30.436875, #divide by average days in a month
            avg_months = floor(avg_age),
            avg_days = floor((avg_age - avg_months) * 30.436875),
            min_age = min_age_days/30.436875,
            min_months = floor(min_age),
            min_days = floor((min_age - min_months) * 30.436875),
            max_age = max_age_days/30.436875,
            max_months = floor(max_age),
            max_days = floor((max_age - max_months) * 30.436875),            
            num_female = sum(gender == 1)) %>%
  select(-avg_age_days, -min_age_days, -max_age_days, -avg_age, -min_age, -max_age)


###-----------------------------------------------FINAL SAMPLE COUNTS PER VOCAB GROUP------------------------------

final_sample_mslist %>%
  filter(age_group == "20 months") %>%
  group_by(language, vocab_group) %>%
  summarize(count = length(unique(recording_name)),
            vocab_median = median(cdi_tot_vocab_prod, na.rm = TRUE), 
            vocab_mean = mean(cdi_tot_vocab_prod, na.rm = TRUE),
            avg_age_days = mean(total_age_days_excel, na.rm = TRUE),
            num_female = sum(gender == 1))

final_sample_mslist %>%
  filter(age_group == "20 months") %>%
  mutate(exclude = case_when(language == "Bilinguals" & is.na(cdi_prod_eng) ~ "exclude",
                             language == "Bilinguals" & is.na(cdi_prod_fr) ~ "exclude",
                             TRUE ~ "keep")) %>%
  filter(exclude == "keep") %>%
  group_by(language) %>%
  summarize(vocab_median = median(total_vocab_prod))



###-----------------------------------------------FINAL SAMPLE COUNTS PER LANG BACKGROUND------------------------------

final_sample_mslist %>% 
  group_by(age_group, language, group) %>%
  summarize(count = length(unique(recording_name)))


###-----------------------------------------------FINAL SAMPLE COUNTS PER EXCLUSION REASON--------------------------

exclusions %>%
  count(age_group, excl_reason) %>%
  arrange(age_group, desc(n))

###----------------------------------------------------------COMPARE GROUPS------------------------------
summary_20 <- final_sample_mslist %>%
  filter(age_group == "20 months")

summary(summary_20$total_age_days_excel)

ggplot(summary_20, aes(total_age_days_excel)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~ language)

t.test(total_age_days_excel ~ language, data = summary_20) # no age diff between mono and bi 20 month olds

###----------------------------------------------------------COMPARE MATERNAL EDUCATION------------------------------

final_sample_mslist %>% 
  mutate(mother_edu = case_when(is.na(mother_edu) ~ "other",
                                TRUE ~ mother_edu)) %>%
  group_by(age_group, language) %>%
  count(mother_edu) %>%
  mutate(pct = n/sum(n)) %>%
  arrange(age_group, language, desc(n))

###--------------------------------------------------Exclusions

# the number of kids who were excluded for different reasons


ms_list_all %>%
  filter(age_group == "20 months") %>%
  filter(recording_name %notin% final_sample_mslist$recording_name) %>%
  mutate(excl_reason = case_when(excl_reason == "none" ~ "inattentive",
                                 TRUE ~ excl_reason)) %>%
  count(age_group, excl_reason)

```




##EyetrackingR Data

```{r eyetrackingR_data, echo = FALSE}

###----------------------------------------------------CREATE EYETRACKINGR DATA FOR FULL TRIAL PLOTS

data_eyetracking_full_trials <- make_eyetrackingr_data(data_full_trials, 
                                participant_column = "recording_name",
                                trial_column = "trial_name", 
                                time_column = "trial_from_zero",
                                trackloss_column = "trackloss",
                                aoi_columns = c('target', 'circle', 'distractor'), # this will calculate prop looking in relation to all AOIs, not just target vs distractor. When I remove circle from here, the plot gets very wonky (I guess because of dividing by 0 in some cases?)
                                treat_non_aoi_looks_as_missing = TRUE)

full_trial_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 0,
                                     window_end_time = 5000, rezero = TRUE, remove = TRUE)

data_time_series_full <- make_time_sequence_data(full_trial_window,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "age_group", "cdi_tot_vocab_prod", "vocab_group", "vocab_centred", "vocab_scaled", "trial_type", "trial_num"),
                                         aois = c("circle", "target", "distractor"))

###---------------------------------------------CREATE EYETRACKINGR DATA FOR ANTICIPATION PERIOD PLOTS

data_eyetracking_antic_window <- subset_by_window(data_eyetracking_full_trials,
                                     window_start_time = 2150,
                                     window_end_time = 3150, rezero = TRUE, remove = TRUE)

trackloss <- trackloss_analysis(data = data_eyetracking_antic_window)

data_eyetracking_clean <- clean_by_trackloss(data = data_eyetracking_antic_window, trial_prop_thresh = TL_PROP) #this eliminates all data from trials with 50% or more trackloss (we merged the baby IDs who made it through to the final sample back with the full data, so makes sense we will re-exclude some trials here)

data_time_series_antic <- make_time_sequence_data(data_eyetracking_clean,
                                         time_bin_size = 200,
                                         predictor_columns = c("language", "age_group", "cdi_tot_vocab_prod", "vocab_group", "vocab_centred", "vocab_scaled", "trial_type", "trial_num"),
                                         aois = c("circle", "target", "distractor"))

```

##Models
###Model data

```{r}

#---------------------------------Model data with time bin 2 as baseline (the middle)

model_data <- data_time_series_antic %>%
  filter(AOI == "target",
         trial_num != 1) %>%
  mutate(trial_num_scaled = trial_num - 2,
         time_bin_centred = TimeBin - 2)

model_data_20_pre <- model_data %>%
  filter(age_group == "20 months",
         trial_type == "pre-switch",
         AOI == "target")

model_data_20_post <- model_data %>%
  filter(age_group == "20 months",
         trial_type == "post-switch",
         AOI == "target")


```


### raw model data plots

For models, we want one data point per baby per trial to use (use made_time_window_data function)

```{r}
#plots with raw data points to compare to model prediction plots later

model_data_20_pre %>% 
  mutate(vocab_grouped = case_when(vocab_centred <= -30 ~ "low",
                                   vocab_centred <= 30 ~ "middle",
                                   vocab_centred > 30 ~ "high"),
         vocab_grouped = factor(vocab_grouped, levels = c("low", "middle", "high"))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(aes(fill = cdi_tot_vocab_prod), alpha = 0.5, shape = 21, stroke = .75) + #don't need vocab stuff anymore
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid(cut_number(vocab_centred, n = 3) ~ language) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_fill_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  labs(color = "trial_num", title = "Infant looking to correct side, Study 2 (Training)")

#ggsave("plot_model_data_20pre_vocab.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in", dpi = 300)

model_data_20_post %>%
  mutate(vocab_grouped = case_when(vocab_centred <= -30 ~ "low",
                                   vocab_centred <= 30 ~ "middle",
                                   vocab_centred > 30 ~ "high"),
         vocab_grouped = factor(vocab_grouped, levels = c("low", "middle", "high"))) %>%
  ggplot(aes(x = TimeBin, y = Prop, color = as.factor(trial_num_scaled))) + 
  geom_jitter(aes(fill = cdi_tot_vocab_prod), alpha = 0.5, shape = 21, stroke = .75) + #don't need vocab stuff anymore
  geom_jitter(alpha = 0.8, shape = 21, stroke = .75) + 
  geom_smooth(aes(color = as.factor(trial_num_scaled)), se = FALSE) + 
  facet_grid(cut_number(vocab_centred, n = 3) ~ language) + 
  facet_grid( ~ language) + 
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_fill_gradient(high = "red", low = "blue", limit = range(c(min(model_data$cdi_tot_vocab_prod, na.rm = TRUE), max(model_data$cdi_tot_vocab_prod, na.rm = TRUE)))) +
  labs(color = "trial_num", title = "Infant looking to correct side, Study 2 (Test)")

#ggsave("plot_model_data_20post_vocab.png", path = here("figures"), device = "png", width = 7, height = 4, units = "in", dpi = 300)



```



###models - 20 m
```{r}

###-------------------------------------------------------------PRE SWITCH 20--------------


#This model is overfitting - let's remove the interaction between vocab and time bin
glmermodel_20pre <- glmer(SamplesInAOI / SamplesTotal ~ language * time_bin_centred * trial_num_scaled + vocab_scaled * trial_num_scaled + vocab_scaled * language + (1 | recording_name), data = model_data_20_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

###-------------------------------------------------------------------FINAL MODEL-------------

final_model_pre_20 <- glmermodel_20pre

###-------------------------------------------------------------POST SWITCH 20--------------

glmermodel_20post <- glmer(SamplesInAOI / SamplesTotal ~ language * time_bin_centred * trial_num_scaled + vocab_scaled * trial_num_scaled + vocab_scaled * language + (1 | recording_name), data = model_data_20_post, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

###-------------------------------------------------------------------FINAL MODEL-------------

final_model_post_20 <- glmermodel_20post


###----------------------------------------------------TABLE OF MODEL RESULTS-----------------

tab_model(final_model_pre_20, show.re.var = FALSE, show.icc = FALSE)
tab_model(final_model_post_20, show.re.var = FALSE, show.icc = FALSE)

##----------------------------------------------------------PLOT OF MODEL RESULTS - GLMER------------

pre20predict <- ggpredict(final_model_pre_20, terms = c("time_bin_centred", "trial_num_scaled", "language", "vocab_scaled"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < -.25 ~ "low vocab",
                           panel > .25 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

pre20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Training phase \nin Study 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(-2, 0, 2), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

#ggsave("plot_model_20_pre_vocab.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in", dpi = 300)

post20predict <- ggpredict(final_model_post_20, terms = c("time_bin_centred", "trial_num_scaled", "language", "vocab_scaled"), type = "fe", ci.lvl = FALSE) %>%
  mutate(vocab = case_when(panel < -.25 ~ "low vocab",
                           panel > .25 ~ "high vocab",
                           TRUE ~ "average vocab")) %>%
  mutate(vocab = factor(vocab, levels = c("low vocab", "average vocab", "high vocab")))

post20predict %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  geom_line() +
  facet_grid(vocab ~ facet) +
  labs(title = "Predicted values of proportion looking to target during the Test phase \nin Study 2 (20 months)", x = "Time in milliseconds during anticipation period", y = "Proportion looking to target", color = "Trial number") +
  scale_color_manual(values = blues, labels = c(2, 3, 4, 5, 6, 7, 8, 9)) +
  scale_x_continuous(breaks = c(-2, 0, 2), labels = c("0", "500", "1000")) +
  ylim(-0.1, 1) +
  theme_ggeffects() +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        panel.spacing = unit(1, "lines"))

#ggsave("plot_model_20_post_vocab.png", path = here("figures"), device = "png", width = 7, height = 7, units = "in", dpi = 300)

```

###Models plus flipped models to compare baseline effects

```{r}
#monolinguals as baseline
tab_model(final_model_pre_20)
tab_model(final_model_post_20)

#bilinguals as baseline (this lets us see the true direction of effects for bilinguals when it's tricky to calculate)
flipped_pre_20 <- glmer(SamplesInAOI / SamplesTotal ~ factor(language, levels = c("Bilinguals", "Monolinguals")) * time_bin_centred * trial_num_scaled + (1 | recording_name), data = model_data_20_pre, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

flipped_post_20 <- glmer(SamplesInAOI / SamplesTotal ~ factor(language, levels = c("Bilinguals", "Monolinguals")) * time_bin_centred * trial_num_scaled (1 | recording_name), data = model_data_20_post, family = binomial, weights = SamplesTotal, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

tab_model(flipped_pre_20)
tab_model(flipped_post_20)

```


##Anovas

###Block data


```{r block_data, echo = FALSE}

###---------------------------------------------------BLOCK DATA----------------------------------

block_data <- data_eyetracking_clean %>%
  make_time_window_data(aois = c("target", "distractor", "circle"),
                        predictor_columns = c("age_group", "language", "cdi_tot_vocab_prod", "vocab_group", "trial_type", "trial_num")) %>%
  select(-Elog, -Weights, -LogitAdjusted, -ArcSin) %>%
  mutate(looking_ms = Prop * (SamplesTotal * (1000/60))) %>% #adds number of milliseconds spent looking at target for the trial
  pivot_wider(names_from = AOI, values_from = c(SamplesInAOI, Prop, looking_ms)) %>%
  mutate(total_looking_time = looking_ms_target + looking_ms_distractor + looking_ms_circle) %>%
  mutate(correct = case_when(looking_ms_target > looking_ms_distractor ~ 1, 
                                   TRUE ~ 0),
         incorrect = case_when(looking_ms_target < looking_ms_distractor ~ 1, 
                                     TRUE ~ 0),
         no_anticipation = case_when(looking_ms_target + looking_ms_distractor == 0 ~ 1, 
                              TRUE ~ 0),
         total_anticipation = 1 - no_anticipation) %>%
  #filter(no_anticipation == 0) %>% ### keep the circle looks!
  mutate(block_num = (as.numeric(trial_num)+2) %/% 3) %>%
  mutate(block_num = as.factor(block_num)) %>%
  group_by(recording_name, language, 
           trial_type, block_num, age_group, vocab_group, cdi_tot_vocab_prod) %>%
  summarise(num_trials_contributed = length(correct), 
            correct_anticipation = mean(correct, na.rm = TRUE),
            total_anticipation = mean(total_anticipation, na.rm = TRUE)) %>%
  group_by(recording_name, trial_type) %>%
  mutate(n_blocks = length(unique(block_num)),
         pooled_vocab_group = ifelse(OVERALL_VOCAB_MEDIAN > cdi_tot_vocab_prod,
                              "Low", 
                              "High"))


block_data_means <- block_data %>%
  group_by(language, age_group, trial_type, block_num) %>%
  summarise(correct_anticipation = mean(correct_anticipation), num_trials_contributed = mean(num_trials_contributed))

#---------------------------------------------------check how many we lose who don't have 3 blocks of data---

block_data %>%
  group_by(age_group) %>%
  filter(n_blocks < 3) %>%
  summarize(dropped = length(unique(recording_name)))
  
```

###Anovas 20 m
```{r}

##---------------------------------------------------------------20 month pre switch
## ANOVA by block: 20m pre-switch


pre_20 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          between = .(language, pooled_vocab_group),
          detailed = TRUE,
          type = 3)

#-----------------------------------------------------------------make table
apa.ezANOVA.table(pre_20,
                  table.number = 6,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the training phase in Experiment 2 (20-month-olds)",
                  filename = here("figures", "anova_table_pre_20_vocab.doc"))

pre_20_mono <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

pre_20_bi <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

#--------------------------------------------------------------------T tests comparing improvement across blocks
#monolingual:
pre_20_mono_t_1_2 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_20_mono_t_1_3 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_20_mono_t_2_3 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#bilingual:

pre_20_bi_t_1_2 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 2) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_20_bi_t_1_3 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 1 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

pre_20_bi_t_2_3 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "pre-switch") %>%
  filter(n_blocks == 3) %>%
  filter(block_num == 2 | block_num == 3) %>%
  t.test(correct_anticipation ~ block_num, data = ., paired = TRUE)

#-------------------------------------------------------------------- T tests comparing mono to bi for each block

pre_20_t_1 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 1) %>%
  t.test(correct_anticipation ~ language, data = .)

pre_20_t_2 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 2) %>%
  t.test(correct_anticipation ~ language, data = .)

pre_20_t_3 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "pre-switch") %>%
  filter(block_num == 3) %>%
  t.test(correct_anticipation ~ language, data = .)
#-----------------------------------------------------------------POST SWITCH 20

## ANOVA by block: 20m post-switch

post_20 <- block_data %>%
  filter(age_group == "20 months") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          between = .(language, pooled_vocab_group),
          detailed = TRUE,
          type = 3)

#-----------------------------------------------------------------make table
apa.ezANOVA.table(post_20,
                  table.number = 7,
                  correction = "none",
                  table.title = "Mixed ANOVA results for the Test phase in Experiment 2 (20-month-olds)",
                  filename = here("figures", "anova_table_post_20_vocab.doc"))

post_20_mono <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Monolinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

post_20_bi <-  block_data %>%
  filter(age_group == "20 months") %>%
  filter(language == "Bilinguals") %>%
  filter(trial_type == "post-switch") %>%
  filter(n_blocks == 3) %>%
  ezANOVA(data = ., 
          dv = correct_anticipation,
          wid = recording_name,
          within = block_num,
          detailed = TRUE,
          type = 3)

```


## Correlation

Check if overall performance correlates across conditions

### Data
```{r}
###----------------------------------------------------Data -----------------
# package for visualization
library("ggpubr")

corr_data <- 
  model_data %>% 
  group_by(trial_type, language, age_group, recording_name) %>% 
  summarise(mean_prop = mean(Prop, na.rm = T)) %>% 
  ungroup() 

# 20
corr_mono_20 <- 
  corr_data %>% 
  filter(language == "Monolinguals", age_group == "20 months") %>% 
  spread(key = trial_type, value = mean_prop) %>%
  rename(postswitch = `post-switch`, preswitch = `pre-switch`)

corr_bi_20 <- 
  corr_data %>% 
  filter(language == "Bilinguals", age_group == "20 months") %>% 
  spread(key = trial_type, value = mean_prop) %>%
  rename(postswitch = `post-switch`, preswitch = `pre-switch`)

###----------------------------------------------------Bilinguals -----------------

# 20-months
# correlations
cor(corr_bi_20$preswitch, corr_bi_20$postswitch, method = "pearson")
cor.test(corr_bi_20$preswitch, corr_bi_20$postswitch, method = "pearson")

# normality assumptions
shapiro.test(corr_bi_20$preswitch) # 0.24
shapiro.test(corr_bi_20$postswitch) # 0.45
ggqqplot(corr_bi_20$preswitch, ylab = "pre-switch")
ggqqplot(corr_bi_20$postswitch, ylab = "post-switch")

# visualization
ggscatter(corr_bi_20, x = "postswitch", y = "preswitch", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "post-switch", ylab = "preswitch")

###----------------------------------------------------Monolinguals -----------------

# 20-months
# correlations
cor(corr_mono_20$preswitch, corr_mono_20$postswitch, method = "pearson")
cor.test(corr_mono_20$preswitch, corr_mono_20$postswitch, method = "pearson")

# normality assumptions
shapiro.test(corr_mono_20$preswitch) # 0.50
shapiro.test(corr_mono_20$postswitch) # 0.03
ggqqplot(corr_mono_20$preswitch, ylab = "pre-switch")
ggqqplot(corr_mono_20$postswitch, ylab = "post-switch")

# visualization
ggscatter(corr_mono_20, x = "postswitch", y = "preswitch", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "post-switch", ylab = "pre-switch")

```

